---
title: "STA-395 - Intro to Machine Learning (Fall '25)"
output:
  html_document:
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: false
---

$~$

Welcome to the website for **Sta-395, Introduction to Machine Learning**! To begin, you can find the course syllabus linked below:

- [Click here](syllabusML25.html) to view the course syllabus

You can locate course content by scrolling, or by using the navigation bar in the upper-left.

## Course Materials

Most class meetings involve both lecture and lab components. Topics are organized into units, which can be found below. The assignments and due-dates for a given week can be found below that week's course materials. Unless otherwise indicated, all assignments are to be submitted via Canvas by 11:59pm.

$~$

### Unit #1 - Concepts, Workflow, and Methods for Tabular Data

#### Week 0/1 - Introduction to Python and `sklearn`

```{r, echo = FALSE, message = FALSE, warning = FALSE}
library(knitr)
library(kableExtra)
library(dplyr)
# x <- cars[1:3,]
# urls <- c("stackoverflow.com", "stats.stackexchange.com", "homebrew.stackexchange.com")
# linkID <- c("link1", "link2", "link3")
# x$website <- paste0("[", linkID, "](http://", urls, ")")
# kable(x)

x = data.frame(Date = c("Th 8/28", "T 9/2", "Th 9/4"), 
               Lecture = c("[Introduction](ml25/intro.pdf)", 
                           "[KNN and Decision Trees](ml25/simple_models.pdf)",
                           "[Data Pre-processing](ml25/preproc.pdf)"),
               Lab = c("[Lab 1 - Crash Course in Python](ml25/Lab_1_F25.html)", 
                       "Finish Lab 1",
                       "[Lab 2 - Introduction to `sklearn`](ml25/Lab_2_F25.html)"),
               Resources = c(" ", " ", " "))
knitr::kable(x, format = "html") %>%
  kable_styling(bootstrap_options = c("hover"))
```

- Lab 1 is due Monday 9/8 at 11:59pm on Canvas
- Lab 2 is due Wednesday 9/10  at 11:59pm on Canvas

$~$

#### Week 2 - Cross-validation and model comparisons

```{r, echo = FALSE, message = FALSE, warning = FALSE}
x = data.frame(Date = c("T 9/9", "Th 9/11"), 
               Lecture = c(" ", 
                           "[Cross-validation](ml25/cv.pdf)"),
               Lab = c("Finish/discuss Lab 2", 
                       "[Lab 3 - Pipelines and Cross-Validation](ml25/Lab_3_F25.html)"),
               Resources = c(" ", " "))
knitr::kable(x, format = "html") %>%
  kable_styling(bootstrap_options = c("hover"))
```

- [Homework 1](ml25/hw1.html) is due Friday 9/12 at 11:59pm on Canvas
- Lab 3 is due Wednesday 9/17 at 11:59pm on Canvas

$~$

#### Week 3 - Classifier performance

```{r, echo = FALSE, message = FALSE, warning = FALSE}
x = data.frame(Date = c("T 9/16", "Th 9/18"), 
               Lecture = c("[Assessing classifier performance](ml25/perform.pdf)",
                           " "),
               Lab = c("Finish/discuss Lab 3",
                       "[Lab 4 - Scoring Metrics](ml25/Lab_4_F25.html)"),
               Resources = c(" ", " "))
knitr::kable(x, format = "html") %>%
  kable_styling(bootstrap_options = c("hover"))
```

- [Homework 2](ml25/hw2.html) is due Monday 9/29 at 11:59pm on Canvas
- Lab 4 is due Wednesday 9/24 at 11:59pm

$~$

#### Week 4 - Regression and machine learning

```{r, echo = FALSE, message = FALSE, warning = FALSE}
x = data.frame(Date = c("T 9/23", "Th 9/25"), 
               Lecture = c("[Feature Transformations and Expansions](ml25/reg1.pdf)",
                           "[Regression for Classification](ml25/reg2.pdf)"),
               Lab = c("Finish/discuss Lab 4",
                       "[Lab 5 - Regression and Machine Learning](ml25/Lab_5_F25.html)"),
               Resources = c(" ", " "))
knitr::kable(x, format = "html") %>%
  kable_styling(bootstrap_options = c("hover"))
```

- Lab 5 is due Wednesday 10/1 at 11:59pm

$~$

#### Week 5 - Regularization

```{r, echo = FALSE, message = FALSE, warning = FALSE}
x = data.frame(Date = c("T 9/30", "Th 10/2"), 
               Lecture = c("[Regularization](ml25/reg3.pdf)",
                           " "),
               Lab = c("Finish/discuss Lab 5",
                       "[Lab 6 - Regularized Regression](ml25/Lab_6_F25.html)"),
               Resources = c(" ", " "))
knitr::kable(x, format = "html") %>%
  kable_styling(bootstrap_options = c("hover"))
```

- Lab 6 is due Wednesday 10/8 at 11:59pm
- [Homework 3](ml25/hw3.html) is due Friday 10/17 at 11:59pm
    - Benchmark scores for this assignment will be released soon
$~$

#### Week 6 - More Models

```{r, echo = FALSE, message = FALSE, warning = FALSE}
x = data.frame(Date = c("T 10/7", "Th 10/9"), 
               Lecture = c("[Support Vector Machines](ml25/svm.pdf)",
                           "[Random Forest](ml25/rf.pdf)"),
               Lab = c("[Lab 7 - Support Vector Machines](ml25/Lab_7_F25.html)",
                       "[Lab 8 - Ensembles and Feature Engineering](ml25/Lab_8_F25.html)"),
               Resources = c("[An Idiot's Guide to SVMs](https://web.mit.edu/6.034/wwwbob/svm.pdf)", " "))
knitr::kable(x, format = "html") %>%
  kable_styling(bootstrap_options = c("hover"))
```

- Lab 7 is due Monday 10/14 
- Lab 8 is due Wednesday 10/16

$~$

#### Week 7 - More Models (cont.)

```{r, echo = FALSE, message = FALSE, warning = FALSE}
x = data.frame(Date = c("T 10/14", "Th 10/16"), 
               Lecture = c("[Gradient Boosting](ml25/boost.pdf)",
                           " "),
               Lab = c("Lab 8 (cont.)",
                       "[Lab 9 - Gradient Boosting with `xgboost`](ml25/Lab_9_F25.html)"),
               Resources = c(" ", " "))
knitr::kable(x, format = "html") %>%
  kable_styling(bootstrap_options = c("hover"))
```

- Lab 9 is due Friday 10/17

$~$

### Unit #2 - Mathematics and "Deep Learning"

#### Week 8 - Gradient Descent Algorithms

```{r, echo = FALSE, message = FALSE, warning = FALSE}
x = data.frame(Date = c("T 10/28", "Th 10/30"), 
               Lecture = c(" ",
                           "[Gradient Descent Algorithms](ml25/grad.pdf)"),
               Lab = c("[Lab 10 - Linear Algebra Review](ml25/Lab_10_F25.html)",
                       " "),
               Resources = c(" ", " "))
knitr::kable(x, format = "html") %>%
  kable_styling(bootstrap_options = c("hover"))
```

- Lab 9 (from before break) is due Wednesday 10/29
- Lab 10 is due Friday 10/31
- [Homework 4](ml25/hw4.html) is due Tuesday 11/11

$~$

#### Week 9 - Neural Networks and Backpropogation

```{r, echo = FALSE, message = FALSE, warning = FALSE}
x = data.frame(Date = c("T 11/4", "Th 11/6"), 
               Lecture = c(" ",
                           "[Neural Networks](ml25/nn.pdf)"),
               Lab = c("[Lab 11 - Gradient Descent Algorithms](ml25/Lab_11_F25.html)",
                       "Finish/discuss Lab 11"),
               Resources = c(" ", " "))
knitr::kable(x, format = "html") %>%
  kable_styling(bootstrap_options = c("hover"))
```

- Lab 11 is due Friday 11/7

$~$

#### Week 10 - Neural Networks

```{r, echo = FALSE, message = FALSE, warning = FALSE}
x = data.frame(Date = c("T 11/11", "Th 11/13"), 
               Lecture = c("",
                           "[Convolutional Neural Networks](ml25/cnn.pdf)"),
               Lab = c("[Lab 12 - Neural Networks in PyTorch](ml25/Lab_12_F25.html)",
                       "[Lab 13 - Convolutional Neural Networks](ml25/Lab_13_F25.html)"),
               Resources = c(" ", " "))
knitr::kable(x, format = "html") %>%
  kable_styling(bootstrap_options = c("hover"))
```

- Lab 12 is due Tuesday 11/18
- Lab 13 will be due after the exam on date that is to be determined

$~$

#### Week 11 - Exam Preparation 

```{r, echo = FALSE, message = FALSE, warning = FALSE}
x = data.frame(Date = c("T 11/18", "Th 11/20"), 
               Lecture = c("Exam Review",
                           " "),
               Lab = c("Finishing up previous labs",
                       "Exam"),
               Resources = c(" ", " "))
knitr::kable(x, format = "html") %>%
  kable_styling(bootstrap_options = c("hover"))
```

- Our exam is on Thursday 11/20. We will have a review session on Tuesday 11/18 and you will be able to retake up to 3 quizzes at the end of the review session.
- [Here is a practice exam](ml25/Practice_Exam.pdf). It is slightly shorter than the actual exam will be, but it should provide a good indication of the format and style of questions used in the actual exam.


$~$

#### Week 12 - More Neural Networks 

```{r, echo = FALSE, message = FALSE, warning = FALSE}
x = data.frame(Date = c("T 11/25", "Th 11/27"), 
               Lecture = c(" ",
                           "No class - Thanksgiving"),
               Lab = c("[Lab 14 - Transfer Learning](ml25/Lab_14_F25.html)",
                       " "),
               Resources = c(" ", " "))
knitr::kable(x, format = "html") %>%
  kable_styling(bootstrap_options = c("hover"))
```

- Lab 13 (CNNs) is due Wednesday 11/26

$~$

#### Week 13 

```{r, echo = FALSE, message = FALSE, warning = FALSE}
x = data.frame(Date = c("T 12/2", "Th 12/4"), 
               Lecture = c("[Recurrent Neural Networks](ml25/rnn.pdf)",
                           " "),
               Lab = c("[Lab 15 - RNNs (optional)](ml25/Lab_15_F25.html)",
                       "Finish Labs 14, 15 and Project Prep"),
               Resources = c(" ", " "))
knitr::kable(x, format = "html") %>%
  kable_styling(bootstrap_options = c("hover"))
```

- Lab 14 is due Friday 12/5
- Lab 15 can be completed for extra credit and I'll accept it any time before Friday 

$~$

#### Week 14

```{r, echo = FALSE, message = FALSE, warning = FALSE}
x = data.frame(Date = c("T 12/9", "Th 12/11"), 
               Lecture = c("Project Presentations #1",
                           "Project Presentations #2"),
               Lab = c(" ",
                       " "),
               Resources = c(" ", " "))
knitr::kable(x, format = "html") %>%
  kable_styling(bootstrap_options = c("hover"))
```

$~$

## Final Project 

[Final Project Description](ml25/final_project.pdf)

- The first project deadline is Tuesday 10/28 - one team member must indicate all members of your project team via email
- The second project deadline is Friday 10/31 - one team member must share a short (1-2 paragraph) proposal via email describing your planned topic, including the data source.
- During Week 13 (the week of Tuesday 12/2) each group is to share an informal, 3-5 minute progress briefing regarding the status of your project. You should be prepared to describe your research aims, data, and current progress. You do not need to prepare any materials or have any formal results yet.



