---
title: "STA-370 - Intro to Machine Learning (Fall '26)"
output:
  html_document:
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: false
---

$~$

Welcome to the website for **Sta-370, Introduction to Machine Learning**! To begin, you can find the course syllabus linked below:

- [Click here](syllabusML26.html) to view the course syllabus

You can locate course content by scrolling, or by using the navigation bar in the upper-left.

## Course Materials

Most class meetings involve both lecture and lab components. Topics are organized into units, which can be found below. The assignments and due-dates for a given week can be found below that week's course materials. Unless otherwise indicated, all assignments are to be submitted via Canvas by 11:59pm.

$~$

### Unit #1 - Concepts, Workflow, and Methods for Tabular Data

#### Week 0/1 - Introduction to Python and `sklearn`

```{r, echo = FALSE, message = FALSE, warning = FALSE}
library(knitr)
library(kableExtra)
library(dplyr)
# x <- cars[1:3,]
# urls <- c("stackoverflow.com", "stats.stackexchange.com", "homebrew.stackexchange.com")
# linkID <- c("link1", "link2", "link3")
# x$website <- paste0("[", linkID, "](http://", urls, ")")
# kable(x)

x = data.frame(Date = c("Th 8/27", "T 9/1", "Th 9/3"), 
               Lecture = c("[Introduction](ml26/intro.pdf)", 
                           "Simple Models",
                           "Data Preprocessing"),
               Lab = c("[Lab 1 - Crash Course in Python](ml26/Lab_1_F26.html)", 
                       "Finish Lab 1",
                       "Lab 2 - Introduction to `sklearn`"),
               Resources = c(" ", " ", " "))
knitr::kable(x, format = "html") %>%
  kable_styling(bootstrap_options = c("hover"))
```

- Lab 1 is due Friday 9/4 at 11:59pm on Canvas
- Lab 2 is due Wednesday 9/9  at 11:59pm on Canvas
- [Homework #1](ml26/hw1.html) is due Tuesday 9/15 at 11:59pm on Canvas

$~$

#### Week 2 - Dimension Reduction

```{r, echo = FALSE, message = FALSE, warning = FALSE}
x = data.frame(Date = c("T 9/8", "Th 9/10"), 
               Lecture = c("Principal Components",
                           " "),
               Lab = c("Lab 3 - Dimension reduction via PCA",
                       "Finish/discuss Lab 3"),
               Resources = c(" ", " "))
knitr::kable(x, format = "html") %>%
  kable_styling(bootstrap_options = c("hover"))
```

- Lab 3 is due Monday 9/14
- Concept Quiz #1 is on Tuesday 9/8 - see the last slide in each of our first three lectures for a list of possible topics

$~$

#### Week 3 - Cross-validation

```{r, echo = FALSE, message = FALSE, warning = FALSE}
x = data.frame(Date = c("T 9/15", "Th 9/17"), 
               Lecture = c("Cross-validation",
                           " "),
               Lab = c("Lab 4 - Pipelines and Cross-validation",
                       "Finish/discuss Lab 4"),
               Resources = c(" ", "[discussion paper](https://robotics.stanford.edu/~ronnyk/accEst.pdf)"))
knitr::kable(x, format = "html") %>%
  kable_styling(bootstrap_options = c("hover"))
```

- Paper discussion #1 is on Thursday 9/17
    - A Study of Cross-Validation and Bootstrap for Accuracy Estimation and Model Selection by Kohavi (1995) 
- Lab 4 is due Monday 9/21

$~$

#### Week 4 - Evaluation Metrics

- Concept Quiz #2 is on Tuesday 9/22 - it will cover PCA and cross-validation (mostly cross-validation)

$~$

#### Week 5 - More Models

- Paper discussion #2 on Thursday 10/1 
    - Statistical Modeling: The Two Cultures by Breiman (2001)

$~$

#### Week 6 - Gradient Boosting

- Concept Quiz #3 is on Tuesday 10/6 - it will cover evaluation metrics and the random forest and SVM algorithms

$~$

#### Week 7 - Explainability

```{r, echo = FALSE, message = FALSE, warning = FALSE}
x = data.frame(Date = c("T 10/13", "Th 10/15"), 
               Lecture = c("Global Importance",
                           "Local Importance"),
               Lab = c("Lab",
                       "Finish/discuss Lab"),
               Resources = c(" ", "[discussion paper](https://robotics.stanford.edu/~ronnyk/accEst.pdf)"))
knitr::kable(x, format = "html") %>%
  kable_styling(bootstrap_options = c("hover"))
```

- Paper discussion #3 on Thursday 10/15
    - "Why Should I Trust You?" Explaining the Predictions of Any Classiﬁer by Ribeiro, Singh, and Guestrin (2016)

$~$

#### Week 8 - Gradient Descent

- Concept Quiz #4 is on Tuesday 10/27 - it will cover gradient boosting and model explainability

$~$

#### Week 9 - Neural Networks

#### Week 10 - More Neural Networks

- Paper discussion #4 on Thursday 11/12
    - ImageNet Classification with Deep Convolutional Neural Networks by Krizhevsky, Sutskever, and Hinton (2012)

#### Week 11 - Exam Prep

- Review session and quiz retakes on Tuesday, exam on Thursday

#### Week 12 - Transfer Learning

#### Week 13 - Transformers 

- Paper discussion #5
    - On the Dangers of Stochastic Parrots:Can Language Models Be Too Big? by Bender, Gebru, McMillan-Major, and Shmitchell (2021)

#### Week 14 - Projects

- Presentations split across Tues/Thurs

$~$

## Final Project 

Coming soon...




