---
title: "STA-395 - Intro to Machine Learning (Fall '25)"
output:
  html_document:
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: false
---

$~$

Welcome to the website for **Sta-395, Introduction to Machine Learning**! To begin, you can find the course syllabus linked below:

- [Click here](syllabusML25.html) to view the course syllabus

You can locate course content by scrolling, or by using the navigation bar in the upper-left.

## Course Materials

Most class meetings involve both lecture and lab components. Topics are organized into units, which can be found below. The assignments and due-dates for a given week can be found below that week's course materials. Unless otherwise indicated, all assignments are to be submitted via Canvas by 11:59pm.

$~$

### Unit #1 - Concepts, Workflow, and Methods for Tabular Data

#### Week 0/1 - Introduction to Python and `sklearn`

```{r, echo = FALSE, message = FALSE, warning = FALSE}
library(knitr)
library(kableExtra)
library(dplyr)
# x <- cars[1:3,]
# urls <- c("stackoverflow.com", "stats.stackexchange.com", "homebrew.stackexchange.com")
# linkID <- c("link1", "link2", "link3")
# x$website <- paste0("[", linkID, "](http://", urls, ")")
# kable(x)

x = data.frame(Date = c("Th 8/28", "T 9/2", "Th 9/4"), 
               Lecture = c("[Introduction](ml25/intro.pdf)", 
                           "[KNN and Decision Trees](ml25/simple_models.pdf)",
                           "[Data Pre-processing](ml25/preproc.pdf)"),
               Lab = c("[Lab 1 - Crash Course in Python](ml25/Lab_1_F25.html)", 
                       "Finish Lab 1",
                       "[Lab 2 - Introduction to `sklearn`](ml25/Lab_2_F25.html)"),
               Resources = c(" ", " ", " "))
knitr::kable(x, format = "html") %>%
  kable_styling(bootstrap_options = c("hover"))
```

- Lab 1 is due Monday 9/8 at 11:59pm on Canvas
- Lab 2 is due Wednesday 9/10  at 11:59pm on Canvas

$~$

#### Week 2 - Cross-validation and model comparisons

```{r, echo = FALSE, message = FALSE, warning = FALSE}
x = data.frame(Date = c("T 9/9", "Th 9/11"), 
               Lecture = c(" ", 
                           "[Cross-validation](ml25/cv.pdf)"),
               Lab = c("Finish/discuss Lab 2", 
                       "[Lab 3 - Pipelines and Cross-Validation](ml25/Lab_3_F25.html)"),
               Resources = c(" ", " "))
knitr::kable(x, format = "html") %>%
  kable_styling(bootstrap_options = c("hover"))
```

- [Homework 1](ml25/hw1.html) is due Friday 9/12 at 11:59pm on Canvas
- Lab 3 is due Wednesday 9/17 at 11:59pm on Canvas

$~$

#### Week 3 - Classifier performance

```{r, echo = FALSE, message = FALSE, warning = FALSE}
x = data.frame(Date = c("T 9/16", "Th 9/18"), 
               Lecture = c("[Assessing classifier performance](ml25/perform.pdf)",
                           " "),
               Lab = c("Finish/discuss Lab 3",
                       "[Lab 4 - Scoring Metrics](ml25/Lab_4_F25.html)"),
               Resources = c(" ", " "))
knitr::kable(x, format = "html") %>%
  kable_styling(bootstrap_options = c("hover"))
```

- [Homework 2](ml25/hw2.html) is due Monday 9/29 at 11:59pm on Canvas
- Lab 4 is due Wednesday 9/24 at 11:59pm

$~$

#### Week 4 - Regression and machine learning

```{r, echo = FALSE, message = FALSE, warning = FALSE}
x = data.frame(Date = c("T 9/23", "Th 9/25"), 
               Lecture = c("[Feature Transformations and Expansions](ml25/reg1.pdf)",
                           "[Regression for Classification](ml25/reg2.pdf)"),
               Lab = c("Finish/discuss Lab 4",
                       "[Lab 5 - Regression and Machine Learning](ml25/Lab_5_F25.html)"),
               Resources = c(" ", " "))
knitr::kable(x, format = "html") %>%
  kable_styling(bootstrap_options = c("hover"))
```

- Lab 5 is due Wednesday 10/1 at 11:59pm

$~$

#### Week 5 - Regularization

```{r, echo = FALSE, message = FALSE, warning = FALSE}
x = data.frame(Date = c("T 9/30", "Th 10/2"), 
               Lecture = c("[Regularization](ml25/reg3.pdf)",
                           " "),
               Lab = c("Finish/discuss Lab 5",
                       "[Lab 6 - Regularized Regression](ml25/Lab_6_F25.html)"),
               Resources = c(" ", " "))
knitr::kable(x, format = "html") %>%
  kable_styling(bootstrap_options = c("hover"))
```

- Lab 6 is due Wednesday 10/8 at 11:59pm
- [Homework 3](ml25/hw3.html) is due Friday 10/17 at 11:59pm
    - Benchmark scores for this assignment will be released soon
$~$

#### Week 6 - More Models

```{r, echo = FALSE, message = FALSE, warning = FALSE}
x = data.frame(Date = c("T 10/7", "Th 10/9"), 
               Lecture = c("[Support Vector Machines](ml25/svm.pdf)",
                           "[Random Forest](ml25/rf.pdf)"),
               Lab = c("[Lab 7 - Support Vector Machines](ml25/Lab_7_F25.html)",
                       "[Lab 8 - Ensembles and Feature Engineering](ml25/Lab_8_F25.html)"),
               Resources = c("[An Idiot's Guide to SVMs](https://web.mit.edu/6.034/wwwbob/svm.pdf)", " "))
knitr::kable(x, format = "html") %>%
  kable_styling(bootstrap_options = c("hover"))
```

- Lab 7 is due Monday 10/14 
- Lab 8 is due Wednesday 10/16

$~$

#### Week 7 - More Models (cont.)

```{r, echo = FALSE, message = FALSE, warning = FALSE}
x = data.frame(Date = c("T 10/14", "Th 10/16"), 
               Lecture = c("[Gradient Boosting](ml25/boost.pdf)",
                           " "),
               Lab = c("Lab 8 (cont.)",
                       "[Lab 9 - Gradient Boosting with `xgboost`](ml25/Lab_9_F25.html)"),
               Resources = c(" ", " "))
knitr::kable(x, format = "html") %>%
  kable_styling(bootstrap_options = c("hover"))
```

- Lab 9 is due Friday 10/17

$~$

### Unit #2 - The Mathematics of "Learning"

#### Week 8 - Gradient Descent Algorithms

```{r, echo = FALSE, message = FALSE, warning = FALSE}
x = data.frame(Date = c("T 10/28", "Th 10/30"), 
               Lecture = c("Gradient Descent",
                           "Mini-batch and Stochastic Gradient Descent"),
               Lab = c("Lab 10 - Linear Algebra Review and Gradient Descent",
                       "Finish/discuss Lab 10"),
               Resources = c(" ", " "))
knitr::kable(x, format = "html") %>%
  kable_styling(bootstrap_options = c("hover"))
```

$~$

#### Week 9 - Neural Networks and Backpropogation

```{r, echo = FALSE, message = FALSE, warning = FALSE}
x = data.frame(Date = c("T 11/4", "Th 11/6"), 
               Lecture = c("Neural Networks",
                           " "),
               Lab = c(" ",
                       "Lab 11 - Neural Networks"),
               Resources = c(" ", " "))
knitr::kable(x, format = "html") %>%
  kable_styling(bootstrap_options = c("hover"))
```

$~$

### Unit #3 - Introduction to Deep Learning

Coming soon

$~$

## Final Project 

Information about the course project will be posted here later in the semester (week 6 or 7)

$~$

## Supplemental Resources

**Unit #1**:

- [UW-Madison SSCC Python Data Wrangling tutorials (balanced)](https://sscc.wisc.edu/sscc/pubs/dwp/Python_Fundamentals.html)
- [Python Data Science Handbook Chapters 2,3,4 (more technical)](https://jakevdp.github.io/PythonDataScienceHandbook/)
- [Stefanie Molin's Pandas workshop tutorials 1, 2 (less technical)](https://github.com/stefmolin/pandas-workshop)
