---
title: "STA-395 - Introduction to Machine Learning (Spring 2023)"
output:
  html_document:
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: false
---

$~$

### Syllabus

Welcome to the course website for Sta-395, Introduction to Machine Learning. To begin, you can find the course syllabus linked below:

- [Click here](syllabus395s23.html) to view the course syllabus

You can locate course content by scrolling, or by using the navigation bar in the upper left.  

Please note: material will not be posted until we've reached that point in the course.

## Course Materials

Most class meetings involve both lecture and lab components.  Topics are grouped into units, which can be found below.  Assignments are generally due at the end of a unit, but I encourage you to complete them as they are made available.

$~$

### Unit #1 

**Introduction and Python Foundations**

```{r, echo = FALSE, message = FALSE, warning = FALSE}
library(knitr)
library(kableExtra)
library(dplyr)
# x <- cars[1:3,]
# urls <- c("stackoverflow.com", "stats.stackexchange.com", "homebrew.stackexchange.com")
# linkID <- c("link1", "link2", "link3")
# x$website <- paste0("[", linkID, "](http://", urls, ")")
# kable(x)

x = data.frame(Date = c("1/24", "1/26"), 
               Lecture = c("[Introduction to Machine Learning](ml23/intro.pdf)", " "),
               Lab = c(" ", "[Python Foundations](ml23/Lab1.html)"))
kable(x) %>%
  kable_styling(bootstrap_options = c("hover"))
```

**Assignments**:

- Lab 1 - due Friday 1/27 by midnight

$~$

### Unit #2 

**Machine Learning Concepts and Workflow**

```{r, echo = FALSE, message = FALSE, warning = FALSE}
library(knitr)
library(kableExtra)
library(dplyr)
# x <- cars[1:3,]
# urls <- c("stackoverflow.com", "stats.stackexchange.com", "homebrew.stackexchange.com")
# linkID <- c("link1", "link2", "link3")
# x$website <- paste0("[", linkID, "](http://", urls, ")")
# kable(x)

x = data.frame(Date = c("1/31", "2/2", "2/7", "2/9", "2/14"), 
               Lecture = c("[k-Nearest Neighbors](ml23/mod.pdf)", "[Cross-Validation](ml23/cv.pdf)", " ", "[Classifier Performance](ml23/cm.pdf)", "[Data Preparation](ml23/fe.pdf)"),
               Lab = c("[kNN and Pre-processing](ml23/lab2a.html)", "[Pipelines, Cross-validation, and Tuning Parameters](ml23/lab2b.html)", " ", "[Classifier Performance](ml23/lab3a.html)", "[Feature Engineering Challenge](ml23/lab3b.html)"))
kable(x) %>%
  kable_styling(bootstrap_options = c("hover"))
```

**Assignments**: 

- All labs are due Friday 2/17 by midnight, you may submit one copy per group (make sure both names are included)
- [Homework #1](ml23/hw1.html) - due Tuesday 2/21 by 1pm

$~$
    
### Unit #3 

**Structured Models and Optimization**

```{r, echo = FALSE, message = FALSE, warning = FALSE}
library(knitr)
library(kableExtra)
library(dplyr)
# x <- cars[1:3,]
# urls <- c("stackoverflow.com", "stats.stackexchange.com", "homebrew.stackexchange.com")
# linkID <- c("link1", "link2", "link3")
# x$website <- paste0("[", linkID, "](http://", urls, ")")
# kable(x)

x = data.frame(Date = c("2/21", "2/23", "2/28", "3/2", "3/7"), 
               Lecture = c("[Regression and Gradient Descent Algorithms](ml23/lm.pdf)", "[Logistic and Softmax Regression](ml23/glm.pdf)", "[Regularization](ml23/lasso.pdf)", "No class (working differently day)", " "),
               Lab = c("[Linear Regression and Gradient Descent](ml23/lab4a.html)", "[Logistic and Softmax Regression](ml23/lab4b.html)", " " , " ", "Lasso, Ridge, and Elastic Net"))
kable(x) %>%
  kable_styling(bootstrap_options = c("hover"))
```

**Assignments**: 

- All labs are due Friday 3/10 by midnight, you may submit one copy per group (make sure both names are included)
- [Homework #2](ml23/hw2.html) - due Tuesday 3/14 by 1pm

$~$

### Unit #4 

**Tree-based Models and Ensembles**

```{r, echo = FALSE, message = FALSE, warning = FALSE}
library(knitr)
library(kableExtra)
library(dplyr)
# x <- cars[1:3,]
# urls <- c("stackoverflow.com", "stats.stackexchange.com", "homebrew.stackexchange.com")
# linkID <- c("link1", "link2", "link3")
# x$website <- paste0("[", linkID, "](http://", urls, ")")
# kable(x)

x = data.frame(Date = c("3/9", "3/14", "3/16"), 
               Lecture = c("Decision Tree Models", "Random Forests", "Boosting"),
               Lab = c("Decision Trees", "Random Forests", "XGBoost Challenge"))
kable(x) %>%
  kable_styling(bootstrap_options = c("hover"))
```

**Assignments**: 

- Due dates TBD

### Unit #5 

**Introduction to Deep Learning**

```{r, echo = FALSE, message = FALSE, warning = FALSE}
library(knitr)
library(kableExtra)
library(dplyr)
# x <- cars[1:3,]
# urls <- c("stackoverflow.com", "stats.stackexchange.com", "homebrew.stackexchange.com")
# linkID <- c("link1", "link2", "link3")
# x$website <- paste0("[", linkID, "](http://", urls, ")")
# kable(x)

x = data.frame(Date = c("-", "-", "-", "-"), 
               Lecture = c("Artificial Neural Networks", "Convolutional Neural Networks", "Transfer Learning", "Recurrent Neural Networks"),
               Lab = c("Intro to PyTorch", "Building a CNN", "Transfer Learning", "Building an RNN"))
kable(x) %>%
  kable_styling(bootstrap_options = c("hover"))
```

**Assignments**: 

- Due dates TBD

$~$

### Unit #6

**Unsupervised Learning**

Coming soon

$~$

## Supplemental Resources

**Unit #1**:

- [UW-Madison SSCC Python Data Wrangling tutorials (balanced)](https://sscc.wisc.edu/sscc/pubs/dwp/Python_Fundamentals.html)
- [Python Data Science Handbook Chapters 2,3,4 (more technical)](https://jakevdp.github.io/PythonDataScienceHandbook/)
- [Stefanie Molin's Pandas workshop tutorials 1, 2 (less technical)](https://github.com/stefmolin/pandas-workshop)
- [Intro to Statistical Learning, Ch2.2 and 2.3 (ML concepts)](https://hastie.su.domains/ISLR2/ISLRv2_website.pdf)

**Unit #2**:

- [Intro to Statistical Learning, Ch2.2 and 3.5 (kNN)](https://hastie.su.domains/ISLR2/ISLRv2_website.pdf)
- [Intro to ML with Python Ch 1 and Ch 2.1 (kNN)](https://github.com/amueller/introduction_to_ml_with_python)
- [Stanford's Intro to Statistical Learning video 5.2 (k-fold CV)](https://www.youtube.com/watch?v=AMfvd_hLssE&list=PLoROMvodv4rOzrYsAxzQyHb8n_RWNuS1e&index=28)
- [Stanford's Intro to Statistical Learning video 5.3 (CV the right and wrong way)](hhttps://www.youtube.com/watch?v=jgoa28FR__Y&list=PLoROMvodv4rOzrYsAxzQyHb8n_RWNuS1e&index=29)
- [Intro to ML with Python Ch 5 (Model Evaluation and Improvement)](https://github.com/amueller/introduction_to_ml_with_python)

**Unit #3**:

- [Intro to ML with Python Ch 2 (Linear Models)](https://github.com/amueller/introduction_to_ml_with_python)
- [Intro to Statistical Learning, Ch 4.2 and 4.3 (Logistic Regression)](https://hastie.su.domains/ISLR2/ISLRv2_website.pdf)
- [Intro to Statistical Learning, Ch 6.2 (Regularization)](https://hastie.su.domains/ISLR2/ISLRv2_website.pdf)
- [Stanford's Intro to Statistical Learning video 6.7 (Lasso)](https://www.youtube.com/watch?v=0tfPuddPhEY&list=PLoROMvodv4rOzrYsAxzQyHb8n_RWNuS1e&index=40)

## Final Project 

The last several weeks of the semester will be devoted to a cumulative final project.  Intermediate deadlines and reminders will be posted here:

- Coming soon

Guidelines and a detailed description of the project are posted below:

- Coming soon