---
title: "STA-395 - Introduction to Machine Learning (Spring 2023)"
output:
  html_document:
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: false
---

$~$

### Syllabus

Welcome to the course website for Sta-395, Introduction to Machine Learning. To begin, you can find the course syllabus linked below:

- [Click here](syllabus395s23.html) to view the course syllabus

You can locate course content by scrolling, or by using the navigation bar in the upper left.  

Please note: material will not be posted until we've reached that point in the course.

## Course Materials

Most class meetings involve both lecture and lab components.  Topics are grouped into units, which can be found below.  Assignments are generally due at the end of a unit, but I encourage you to complete them as they are made available.

$~$

### Unit #1 

**Introduction and Python Foundations**

```{r, echo = FALSE, message = FALSE, warning = FALSE}
library(knitr)
library(kableExtra)
library(dplyr)
# x <- cars[1:3,]
# urls <- c("stackoverflow.com", "stats.stackexchange.com", "homebrew.stackexchange.com")
# linkID <- c("link1", "link2", "link3")
# x$website <- paste0("[", linkID, "](http://", urls, ")")
# kable(x)

x = data.frame(Date = c("1/24", "1/26"), 
               Lecture = c("[Introduction to Machine Learning](ml23/intro.pdf)", " "),
               Lab = c(" ", "[Python Foundations](ml23/Lab1.html)"))
kable(x) %>%
  kable_styling(bootstrap_options = c("hover"))
```

**Assignments**:

- Lab 1 - due Friday 1/27 by midnight

$~$

### Unit #2 

**Machine Learning Concepts and Workflow**

```{r, echo = FALSE, message = FALSE, warning = FALSE}
library(knitr)
library(kableExtra)
library(dplyr)
# x <- cars[1:3,]
# urls <- c("stackoverflow.com", "stats.stackexchange.com", "homebrew.stackexchange.com")
# linkID <- c("link1", "link2", "link3")
# x$website <- paste0("[", linkID, "](http://", urls, ")")
# kable(x)

x = data.frame(Date = c("1/31", "2/2", "2/7", "2/9", "2/14"), 
               Lecture = c("[k-Nearest Neighbors](ml23/mod.pdf)", "[Cross-Validation](ml23/cv.pdf)", " ", "[Classifier Performance](ml23/cm.pdf)", "[Data Preparation](ml23/fe.pdf)"),
               Lab = c("[kNN and Pre-processing](ml23/lab2a.html)", "[Pipelines, Cross-validation, and Tuning Parameters](ml23/lab2b.html)", " ", "[Classifier Performance](ml23/lab3a.html)", "[Feature Engineering Challenge](ml23/lab3b.html)"))
kable(x) %>%
  kable_styling(bootstrap_options = c("hover"))
```

**Assignments**: 

- All labs are due Friday 2/17 by midnight, you may submit one copy per group (make sure both names are included)
- [Homework #1](ml23/hw1.html) - due Tuesday 2/21 by 1pm

$~$
    
### Unit #3 

**Structured Models and Optimization**

```{r, echo = FALSE, message = FALSE, warning = FALSE}
library(knitr)
library(kableExtra)
library(dplyr)
# x <- cars[1:3,]
# urls <- c("stackoverflow.com", "stats.stackexchange.com", "homebrew.stackexchange.com")
# linkID <- c("link1", "link2", "link3")
# x$website <- paste0("[", linkID, "](http://", urls, ")")
# kable(x)

x = data.frame(Date = c("2/21", "2/23", "2/28", "3/2", "3/7", "3/9"), 
               Lecture = c("[Regression and Gradient Descent Algorithms](ml23/lm.pdf)", "[Logistic and Softmax Regression](ml23/glm.pdf)", "[Regularization](ml23/lasso.pdf)", "No class (working differently day)", " ", "[Feature Expansion](ml23/splines.pdf)"),
               Lab = c("[Linear Regression and Gradient Descent](ml23/lab4a.html)", "[Logistic and Softmax Regression](ml23/lab4b.html)", " " , " ", "[Lasso, Ridge, and Elastic Net](ml23/lab5a.html)", "[Discretization, Polynomials, and Splines](ml23/lab5b.html)"))
kable(x) %>%
  kable_styling(bootstrap_options = c("hover"))
```

**Assignments**: 

- All labs are due Friday 3/10 by midnight, you may submit one copy per group (make sure both names are included)
- [Homework #2](ml23/hw2.html) - due Tuesday 3/14 by 1pm

$~$

### Unit #4 

**Tree-based Models and Ensembles**

```{r, echo = FALSE, message = FALSE, warning = FALSE}
library(knitr)
library(kableExtra)
library(dplyr)
# x <- cars[1:3,]
# urls <- c("stackoverflow.com", "stats.stackexchange.com", "homebrew.stackexchange.com")
# linkID <- c("link1", "link2", "link3")
# x$website <- paste0("[", linkID, "](http://", urls, ")")
# kable(x)

x = data.frame(Date = c("3/14", "3/16", "4/4"), 
               Lecture = c("[Decision Tree Models](ml23/trees.pdf)", "[Random Forests](ml23/rf.pdf)", "[Boosting](ml23/boosting.pdf)"),
               Lab = c("[Decision Trees](ml23/lab6a.html)", "[Ensembles, Stacking, and Random Forests](ml23/lab6b.html)", "[Boosting and `xgboost`](ml23/lab7.html)"))
kable(x) %>%
  kable_styling(bootstrap_options = c("hover"))
```

**Assignments**: 

- Labs 6 (parts 1 and 2) and 7 (single part) are due Friday 4/7 by midnight
- [Optional Lab](ml23/prereq.html) for 3 points of quiz extra credit if completed by Tuesday 4/4 at 1pm
- [Homework #3](ml23/hw3.html) - due Tuesday 4/11 by 1pm

### Unit #5 

**Introduction to Deep Learning**

```{r, echo = FALSE, message = FALSE, warning = FALSE}
library(knitr)
library(kableExtra)
library(dplyr)

x = data.frame(Date = c("4/11", "-", "-", "-"), 
               Lecture = c("[Artificial Neural Networks](ml23/ann.pdf)", "Convolutional Neural Networks", "Transfer Learning", "Recurrent Neural Networks"),
               Lab = c("[Tensors and PyTorch](ml23/lab8a.html)", "Building a CNN", "Transfer Learning", "Building an RNN"))
kable(x) %>%
  kable_styling(bootstrap_options = c("hover"))
```

**Assignments**: 

- Lab 8 (parts 1 and 2) due Friday 4/21 by 11:59pm
- Lab 9 (parts 1 and 2) due Friday 4/28 by 11:59pm
- [Homework #4](ml23/hw4.html) - due Tuesday 5/2 by 1pm

$~$

### Unit #6

**Introduction to Unsupervised Learning** (time permitting, optional lectures and labs)

- Coming soon 

$~$

## Supplemental Resources

**Unit #1**:

- [UW-Madison SSCC Python Data Wrangling tutorials (balanced)](https://sscc.wisc.edu/sscc/pubs/dwp/Python_Fundamentals.html)
- [Python Data Science Handbook Chapters 2,3,4 (more technical)](https://jakevdp.github.io/PythonDataScienceHandbook/)
- [Stefanie Molin's Pandas workshop tutorials 1, 2 (less technical)](https://github.com/stefmolin/pandas-workshop)
- [Intro to Statistical Learning, Ch 2.2 and 2.3 (ML concepts)](https://hastie.su.domains/ISLR2/ISLRv2_website.pdf)

**Unit #2**:

- [Intro to Statistical Learning, Ch 2.2 and 3.5 (kNN)](https://hastie.su.domains/ISLR2/ISLRv2_website.pdf)
- [Intro to ML with Python Ch 1 and Ch 2.1 (kNN)](https://github.com/amueller/introduction_to_ml_with_python)
- [Stanford's Intro to Statistical Learning video 5.2 (k-fold CV)](https://www.youtube.com/watch?v=AMfvd_hLssE&list=PLoROMvodv4rOzrYsAxzQyHb8n_RWNuS1e&index=28)
- [Stanford's Intro to Statistical Learning video 5.3 (CV the right and wrong way)](hhttps://www.youtube.com/watch?v=jgoa28FR__Y&list=PLoROMvodv4rOzrYsAxzQyHb8n_RWNuS1e&index=29)
- [Intro to ML with Python Ch 5 (Model Evaluation and Improvement)](https://github.com/amueller/introduction_to_ml_with_python)

**Unit #3**:

- [Intro to ML with Python Ch 2 (Linear Models)](https://github.com/amueller/introduction_to_ml_with_python)
- [Intro to Statistical Learning, Ch 4.2 and 4.3 (Logistic Regression)](https://hastie.su.domains/ISLR2/ISLRv2_website.pdf)
- [Intro to Statistical Learning, Ch 6.2 (Regularization)](https://hastie.su.domains/ISLR2/ISLRv2_website.pdf)
- [Stanford's Intro to Statistical Learning video 6.7 (Lasso)](https://www.youtube.com/watch?v=0tfPuddPhEY&list=PLoROMvodv4rOzrYsAxzQyHb8n_RWNuS1e&index=40)

**Unit #4**: 

- [Intro to Statistical Learning, Ch 8 (Decision Tree Models)](https://hastie.su.domains/ISLR2/ISLRv2_website.pdf)
- [Stanford's Intro to Statistical Learning video 8.4 (Bagging and Random Forest)](https://www.youtube.com/watch?v=_cKAxjnInfA&list=PLoROMvodv4rOzrYsAxzQyHb8n_RWNuS1e&index=57)
- [Stanford's Intro to Statistical Learning video 8.5 (Boosting)](https://www.youtube.com/watch?v=_cKAxjnInfA&list=PLoROMvodv4rOzrYsAxzQyHb8n_RWNuS1e&index=58)
- [Google's Intro to Gradient Boosted Trees](https://developers.google.com/machine-learning/decision-forests/intro-to-gbdt)

**Unit #5**:

- [Intro to Statistical Learning, Ch 10 (Deep Learning)](https://hastie.su.domains/ISLR2/ISLRv2_website.pdf)
- [Stanford Engineering Intro to Neural Networks (CS229)](https://www.youtube.com/watch?v=MfIjxPh6Pys)
- [PyTorch - Learning the Basics](https://pytorch.org/tutorials/beginner/basics/intro.html)

## Final Project 

The last several weeks of the semester will be devoted to a cumulative final project.  Intermediate deadlines and reminders will be posted here:

- First deadline - Choose your project partner(s) by Monday 4/10

Guidelines and a detailed description of the project are posted below:

- [Link to guidelines](ml23/final_project.pdf)