---
title: "STA-209 - Applied Statistics (Fall 2025)"
output:
  html_document:
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: false
---

$~$

Welcome to the course website for Sta-209-02 (Applied Statistics). You can find the course syllabus linked below:

- [Click here](syllabus209f25.html) to view the course syllabus

You can locate course content by scrolling, or by using the navigation bar in the upper left.  

Please note that some material will not be posted until we've reached that point in the course.

## Course Materials

Course meetings typically involve a short lecture followed by a lab activity. The labs from a given week are generally due on Friday, and the corresponding homework assignment is due on the following Monday. Unless otherwise mentioned, all assignments are due by 11:59pm (midnight) on their due date.

$~$

### Exam #1 Content

**Week 0/1** - Statistical Thinking and Simple Hypothesis Tests

```{r, echo = FALSE, message = FALSE, warning = FALSE}
library(knitr)
library(kableExtra)
library(dplyr)
# x <- cars[1:3,]
# urls <- c("stackoverflow.com", "stats.stackexchange.com", "homebrew.stackexchange.com")
# linkID <- c("link1", "link2", "link3")
# x$website <- paste0("[", linkID, "](http://", urls, ")")
# kable(x)

x = data.frame(Date = c("Fri 8/29", "Mon 9/1", "Wed 9/3", "Fri 9/5"), 
               Lecture = c("[Introduction to Statistical Thinking](s209f25/intro.pdf)", 
                           "No class (Labor Day)",
                           "[Hypothesis Testing](s209f25/ht1.pdf)",
                           " "),
               Lab = c("[Lab 1 - A first hypothesis test](s209f25/first_test.html)", 
                       "  ",
                       "Finish/discuss Lab 1",
                       "[Lab 2 - Intro to `R` and one-sample categorical data](s209f25/one_sample_cat.html)"),
               Resources = c(" ", " ", "[`R` Basics from Modern Statistics with R](https://www.modernstatisticswithr.com/thebasics.html)", " "))
knitr::kable(x, format = "html") %>%
  kable_styling(bootstrap_options = c("hover"))
```

**Assignments and Deadlines**:

- Labs 1 and 2 are due Friday 9/5 by 11:59pm (submit via Canvas)
- [Homework 1](s209f25/hw1.html) is due Monday 9/8 (submit via Canvas)

$~$

**Week 2** - More Hypothesis Testing

```{r, echo = FALSE, message = FALSE, warning = FALSE}
x = data.frame(Date = c("Mon 9/8", "Wed 9/10", "Fri 9/12"), 
               Lecture = c(" ", 
                           "[One-sample Z and T tests](s209f25/ht2.pdf)",
                           " "),
               Lab = c("[Lab 3 - More `R` and one-sample quantitative data](s209f25/more_R.html)", 
                       "Finish/discuss Lab 3",
                       "[Lab 4 - One-sample hypothesis tests in `R`](s209f25/Z_and_T.html)"),
               Resources = c("[Data visualization from R for Data Science](https://r4ds.hadley.nz/layers.html) and [`ggplot` Cheatsheet](https://posit.co/wp-content/uploads/2022/10/data-visualization-1.pdf)", "[IMS Z-test for a single proportion](https://openintro-ims.netlify.app/inference-one-prop#hypothesis-test-for-a-proportion)", " "))
knitr::kable(x, format = "html") %>%
  kable_styling(bootstrap_options = c("hover"))
```

**Assignments and Deadlines**:

- Lab 3 is due Friday 9/12 by 11:59pm
- Lab 4 is due Monday 9/15 by 11:59pm
- [Homework 2](s209f25/hw2.html) is due Monday 9/15 by 11:59pm

$~$

**Week 3** - Two-sample Tests

```{r, echo = FALSE, message = FALSE, warning = FALSE}
x = data.frame(Date = c("Mon 9/15", "Wed 9/17", "Fri 9/19"), 
               Lecture = c("", 
                           "[Two-sample Z and T tests](s209f25/ht3.pdf)",
                           " "),
               Lab = c("Finish/discuss Lab 4", 
                       "[Lab 5 - Analyzing two-sample data in `R`](s209f25/two_sample.html)",
                       "Finish/discuss Lab 5"),
               Resources = c(" " , " ", " "))
knitr::kable(x, format = "html") %>%
  kable_styling(bootstrap_options = c("hover"))
```

- Lab 5 is due Monday 9/22 at 11:59pm
- [Homework 3](s209f25/hw3.html) is due Monday 9/22 by 11:59pm

$~$

**Week 4** - Correlation and Regression

```{r, echo = FALSE, message = FALSE, warning = FALSE}
x = data.frame(Date = c("Mon 9/22", "Wed 9/24", "Fri 9/26"), 
               Lecture = c("[Correlation](s209f25/cor.pdf)", 
                           "[Simple Linear Regression](s209f25/reg.pdf)",
                           " "),
               Lab = c("", 
                       "[Lab 6 - Correlation and Simple Linear Regression](s209f25/cor_reg.html)",
                       "Finish/discuss Lab 6"),
               Resources = c(" " , " ", " "))
knitr::kable(x, format = "html") %>%
  kable_styling(bootstrap_options = c("hover"))
```

- Lab 6 is due Monday 9/29
- [Homework 4](s209f25/hw4.html) is due Monday 9/29
- We have our first exam next week ([practice version](s209f25/Exam1_Practice.pdf))
    - [Exam 1 study guide](s209f25/Exam_1_study_guide.pdf) 

$~$ 

**Week 5** - Wrap-up and Exam 1

```{r, echo = FALSE, message = FALSE, warning = FALSE}
x = data.frame(Date = c("Mon 9/29", "Wed 10/1", "Fri 10/3"), 
               Lecture = c("[Study Design and Contingency Tables](s209f25/design.pdf)", 
                           " ",
                           "Exam 1"),
               Lab = c(" ", 
                       "Review Session",
                       " "),
               Resources = c(" " , " ", " "))
knitr::kable(x, format = "html") %>%
  kable_styling(bootstrap_options = c("hover"))
```

- [Practice Exam 1](s209f25/Exam1_Practice.pdf) 
   - [Practice Exam Solutions](s209f25/Exam1_soln.pdf) 

$~$ 

### Exam #2 Content

**Week 6** - Contingency Tables and Chi-Squared Tests

```{r, echo = FALSE, message = FALSE, warning = FALSE}
x = data.frame(Date = c("Mon 10/6", "Wed 10/8", "Fri 10/10"), 
               Lecture = c("[Study Design and Contingency Tables (continued)](s209f25/design.pdf)", 
                           " ",
                           "[Chi-squared Tests (Part 1 - Goodness of Fit)](s209f25/chisq1.pdf)"),
               Lab = c("[Lab 7 - Contingency Tables](s209f25/tables.html)", 
                       "Finish/discuss Lab 7",
                       "[Lab 8 - Chi-squared Tests](s209f25/chisq.html)"),
               Resources = c(" " , " ", " "))
knitr::kable(x, format = "html") %>%
  kable_styling(bootstrap_options = c("hover"))
```

- Lab 7 is due Friday 10/10
- Lab 8 is due Wednesday 10/15
- [Homework 5](s209f25/hw5.html) is due Wednesday 10/15

$~$

**Week 7**: Analysis of Variance

```{r, echo = FALSE, message = FALSE, warning = FALSE}
x = data.frame(Date = c("Mon 10/13", "Wed 10/15", "Fri 10/17"), 
               Lecture = c("[Chi-squared Tests (Part 2 - Independence)](s209f25/chisq2.pdf)", 
                           "[One-way ANOVA](s209f25/anova.pdf)",
                           " "),
               Lab = c("Finish/discuss Lab 8", 
                       "[Lab 9 - ANOVA](s209f25/anova.html)",
                       "Finish/discuss Lab 9"),
               Resources = c(" " , " ", " "))
knitr::kable(x, format = "html") %>%
  kable_styling(bootstrap_options = c("hover"))
```

- Lab 8 is due Wednesday 10/15
- Lab 9 is due Friday 10/17
- [Homework 6](s209f25/hw6.html) is due Monday 11/3
    - *Note*: this assignment will eventually contain three questions, but I'm posting the question focused on ANOVA in case you wanted to work on it.

$~$

 **Week 8**: Multiple Comparisons and Data Transformations

```{r, echo = FALSE, message = FALSE, warning = FALSE}
x = data.frame(Date = c("Mon 10/27", "Wed 10/29", "Fri 10/31"), 
               Lecture = c("[Testing Errors and Multiple Comparisons](s209f25/mcomp.pdf)", 
                           " ",
                           " "),
               Lab = c("[Lab 10 - Outliers, Transformations, and Multiple Comparisons](s209f25/mcomp_trans.html)", 
                       "Finish/discuss Lab 10",
                       "Project Exploratory Analysis"),
               Resources = c("[UVA article on interpretting log-transformations](https://library.virginia.edu/data/articles/interpreting-log-transformations-in-a-linear-model)" , " ", " "))
knitr::kable(x, format = "html") %>%
  kable_styling(bootstrap_options = c("hover"))
```

- [Homework 6](s209f25/hw6.html) is due Monday 11/3
- Lab 10 is due Friday 10/31
- An exploratory analysis of your project data is due Friday 10/31. If you are collecting your own data you should aim to have at least some of it collected before then.

$~$

**Week 9**: Confidence Intervals

```{r, echo = FALSE, message = FALSE, warning = FALSE}
x = data.frame(Date = c("Mon 11/3", "Wed 11/5", "Fri 11/7"), 
               Lecture = c("[Confidence Intervals](s209f25/ci.pdf)", 
                           " ",
                           "[Bootstrapping](s209f25/boot.pdf)"),
               Lab = c("[Lab 11 - Confidence Intervals](s209f25/ci1.html)", 
                       "Finish/discuss Lab 11",
                       " "),
               Resources = c(" " , " ", "[IMS chapter on Bootstrapping](https://openintro-ims.netlify.app/foundations-bootstrapping)"))
knitr::kable(x, format = "html") %>%
  kable_styling(bootstrap_options = c("hover"))
```


- [Homework 7](s209f25/hw7.html) is due Monday 11/10
- Lab 11 is due Friday 11/7
- Exam 2 is next Friday
    - [Practice Exam 2](s209f25/Practice_Exam2.pdf) 
    - [Study Guide](s209f25/Exam_2_study_guide.pdf) 

$~$

**Week 10**: Wrap-up and Exam 2

```{r, echo = FALSE, message = FALSE, warning = FALSE}
x = data.frame(Date = c("Mon 11/10", "Wed 11/12", "Fri 11/14"), 
               Lecture = c(" ", 
                           "Exam 2 Review",
                           "Exam 2"),
               Lab = c("[Lab 12 - Bootstrapping](s209f25/ci2.html)", 
                       "Finish/discuss Lab 12 (if needed)",
                       " "),
               Resources = c(" " , " ", " "))
knitr::kable(x, format = "html") %>%
  kable_styling(bootstrap_options = c("hover"))
```

- There is no homework assignment this week due to Exam 2
- Lab 12 is due Wednesday 11/12
- Exam 2 is Friday 11/14
    - [Practice Exam 2](s209f25/Practice_Exam2.pdf) 
        - [Sketch Solution](s209f25/Practice_Exam2_soln.pdf)
    - [Study Guide](s209f25/Exam_2_study_guide.pdf) 

$~$



## Tentative Exam Dates

- Exam 1 - Friday 10/3
- Exam 2 - Friday 11/14
- Exam 3 - Monday 12/8

$~$

## Project 

Information and deadlines for the course project are [found here](s209f25/project.html)

- ~~The first deadline is to decide upon your group members (2 or 3 people per group) by Monday 10/6~~
- ~~The second deadline will be to submit a proposal for your project topic by Friday 10/10~~
- ~~The third deadline is to submit your exploratory analysis by Friday 10/31~~
- Project presentations will take place on Wed 12/10 and Fri 12/12. There will be one class meeting in Decemeber where you will have an opportunity to work on your project and discuss your final analyses with me.