---
title: "STA-209 - Applied Statistics (Fall 2025)"
output:
  html_document:
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: false
---

$~$

Welcome to the course website for Sta-209-02 (Applied Statistics). You can find the course syllabus linked below:

- [Click here](syllabus209f25.html) to view the course syllabus

You can locate course content by scrolling, or by using the navigation bar in the upper left.  

Please note that some material will not be posted until we've reached that point in the course.

## Course Materials

Course meetings typically involve a short lecture followed by a lab activity. The labs from a given week are generally due on Friday, and the corresponding homework assignment is due on the following Monday. Unless otherwise mentioned, all assignments are due by 11:59pm (midnight) on their due date.

$~$

### Exam #1 Content

**Week 0/1** - Statistical Thinking and Simple Hypothesis Tests

```{r, echo = FALSE, message = FALSE, warning = FALSE}
library(knitr)
library(kableExtra)
library(dplyr)
# x <- cars[1:3,]
# urls <- c("stackoverflow.com", "stats.stackexchange.com", "homebrew.stackexchange.com")
# linkID <- c("link1", "link2", "link3")
# x$website <- paste0("[", linkID, "](http://", urls, ")")
# kable(x)

x = data.frame(Date = c("Fri 8/29", "Mon 9/1", "Wed 9/3", "Fri 9/5"), 
               Lecture = c("[Introduction to Statistical Thinking](s209f25/intro.pdf)", 
                           "No class (Labor Day)",
                           "[Hypothesis Testing](s209f25/ht1.pdf)",
                           " "),
               Lab = c("[Lab 1 - A first hypothesis test](s209f25/first_test.html)", 
                       "  ",
                       "Finish/discuss Lab 1",
                       "[Lab 2 - Intro to `R` and one-sample categorical data](s209f25/one_sample_cat.html)"),
               Resources = c(" ", " ", "[`R` Basics from Modern Statistics with R](https://www.modernstatisticswithr.com/thebasics.html)", " "))
knitr::kable(x, format = "html") %>%
  kable_styling(bootstrap_options = c("hover"))
```

**Assignments and Deadlines**:

- Labs 1 and 2 are due Friday 9/5 by 11:59pm (submit via Canvas)
- [Homework 1](s209f25/hw1.html) is due Monday 9/8 (submit via Canvas)

$~$

**Week 2** - More Hypothesis Tests

```{r, echo = FALSE, message = FALSE, warning = FALSE}
x = data.frame(Date = c("Mon 9/8", "Wed 9/10", "Fri 9/12"), 
               Lecture = c(" ", 
                           "Z and T tests",
                           "Z and T tests (cont.)"),
               Lab = c("[Lab 3 - More `R` and one-sample quantitative data](s209f25/more_R.html)", 
                       "Lab 4 - Data manipulation and hypothesis tests in `R`",
                       "Finish Lab 4"),
               Resources = c("[Data visualization from R for Data Science](https://r4ds.hadley.nz/layers.html) and [`ggplot` Cheatsheet](https://posit.co/wp-content/uploads/2022/10/data-visualization-1.pdf)", " ", " "))
knitr::kable(x, format = "html") %>%
  kable_styling(bootstrap_options = c("hover"))
```

**Assignments and Deadlines**:

- Labs 4 and 5 are due Friday 9/12 by 11:59pm
- Homework 2 is due Monday 9/15

$~$

## Tentative Exam Dates

- Exam 1 - Friday 10/3
- Exam 2 - Friday 11/14
- Exam 3 - Monday 12/8

$~$

## Project 

Information and deadlines for the course project will be posted here. Right now there are no upcoming deadlines.