---
title: "STA-209 - Applied Statistics (Fall 2026)"
output:
  html_document:
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: false
---

$~$

Welcome to the course website for Sta-209-04 (Applied Statistics). You can find the course syllabus linked below:

- [Click here](syllabus209f26.html) to view the course syllabus

You can locate course content by scrolling, or by using the navigation bar in the upper left.  

Please note that some material will not be posted until we've reached that point in the course.

## Course Materials

Course meetings typically involve a short lecture followed by a lab activity. Unless otherwise mentioned, all assignments are due by 11:59pm (midnight) on their due date.

$~$

### Exam #1 Content

**Week 0/1** - Statistical Thinking and Simple Hypothesis Tests

```{r, echo = FALSE, message = FALSE, warning = FALSE}
library(knitr)
library(kableExtra)
library(dplyr)
# x <- cars[1:3,]
# urls <- c("stackoverflow.com", "stats.stackexchange.com", "homebrew.stackexchange.com")
# linkID <- c("link1", "link2", "link3")
# x$website <- paste0("[", linkID, "](http://", urls, ")")
# kable(x)

x = data.frame(Date = c("Fri 8/28", "Mon 8/31", "Wed 9/2", "Fri 9/4"), 
               Lecture = c("[Statistical Thinking and Probability](s209f26/intro.pdf)", 
                           "[Hypothesis Testing (part 1: sampling)](s209f26/ht1.pdf)",
                           " ",
                           " "),
               Lab = c("[Lab 1 - A first hypothesis test](s209f26/first_test.html)", 
                       "Finish/discuss Lab 1",
                       "Lab 2 - Intro to `R` and one-sample categorical data",
                       "Lab 3 - More `R` and one-sample quantitative data"),
               Resources = c(" ", "[Ch 2.1 - Sampling Principles from Intro to Modern Statistics](https://openintrostat.github.io/ims/data-design.html) ", "[`R` Basics from Modern Statistics with R](https://www.modernstatisticswithr.com/thebasics.html)", " "))
knitr::kable(x, format = "html") %>%
  kable_styling(bootstrap_options = c("hover"))
```

**Assignments and Deadlines**:

- Lab 1 is due Monday 8/31
- Labs 2 and 3 are due Wednesday 9/7
- [Homework 1](s209f26/hw1.html) is due Friday 9/4 

All assignments should be submitted via Canvas.

$~$

**Week 2** - More Hypothesis Testing

```{r, echo = FALSE, message = FALSE, warning = FALSE, eval = FALSE}
x = data.frame(Date = c("Mon 9/7", "Wed 9/2", "Fri 9/4"), 
               Lecture = c("No classes - Labor Day", 
                           "One-sample Z-tests",
                           "One-sample T-tests"),
               Lab = c(" - ",
                       "Lab 4 - One-sample tests in `R`",
                       "Finish/discuss Lab 4"),
               Resources = c(" ", " ", " "))
knitr::kable(x, format = "html") %>%
  kable_styling(bootstrap_options = c("hover"))
```


$~$

## Exam Dates

Study materials (practice test, study guide, etc.) will be released approximately 1-week prior to each exam.

- Exam 1 - Friday 10/2
- Exam 2 - Friday 11/13
- Exam 3 - Monday 12/7

$~$

## Project 

Information and deadlines for the course project will appear here. The project will not formally be introduced until after Exam 1.