---
title: "STA-209 - Applied Statistics (Spring 2024)"
output:
  html_document:
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: false
---

$~$

Welcome to the course website for Sta-209-04 (Applied Statistics). You can find the course syllabus linked below:

- [Click here](syllabus209s24.html) to view the course syllabus

You can locate course content by scrolling, or by using the navigation bar in the upper left.  

Please note that some material will not be posted until we've reached that point in the course.

## Course Materials

Most class meetings involve both lecture and lab components. Partners will be assigned for each lab. Labs will generally be due 1-2 class meetings after they are assigned, while homework is consistently due every Friday at midnight (with some exceptions surrounding exams).

$~$

### Exam #1 Content

**Week 1**:

```{r, echo = FALSE, message = FALSE, warning = FALSE}
library(knitr)
library(kableExtra)
library(dplyr)
# x <- cars[1:3,]
# urls <- c("stackoverflow.com", "stats.stackexchange.com", "homebrew.stackexchange.com")
# linkID <- c("link1", "link2", "link3")
# x$website <- paste0("[", linkID, "](http://", urls, ")")
# kable(x)

x = data.frame(Date = c("Mon 1/22", "Wed 1/24", "Fri 1/26"), 
               Lecture = c("[Data Basics](s209s24/data_basics.pdf)", 
                           "[Data Visualization](s209s24/data_viz.pdf)",
                           " "),
               Lab = c("[Introduction to `R`](s209s24/R_basics.html)", 
                       "[Data Visualization (part 1)](s209s24/ggplot1.html)",
                       "Data Visualization (part 2)"))
kable(x) %>%
  kable_styling(bootstrap_options = c("hover"))
```

**Assignments and Deadlines (week 1)**:

- The Introduction to `R` and Data Visualization labs
    - Due ~~Monday 1/29~~ Wednesday 1/31 at 11:59pm (via P-web)
- [Homework 1](s209s24/hw1.html) 
    - Due ~~Friday 1/26~~ Tuesday 1/30 at 11:59pm (via P-web)

$~$

**Week 2**:

```{r, echo = FALSE, message = FALSE, warning = FALSE}
x = data.frame(Date = c("Mon 1/29", "Wed 1/31", "Fri 2/2"), 
               Lecture = c("", 
                           "[Descriptive statistics (categorical data)](s209s24/descriptive_stats.pdf)",
                           "[More on contingency tables](s209s24/more_contingency.html)"),
               Lab = c("[Extra credit lab](s209s24/ggplot2.html)", 
                       "[R Markdown and Tables](s209s24/tables.html)",
                       " "))
kable(x) %>%
  kable_styling(bootstrap_options = c("hover"))
```

**Assignments and Deadlines (week 2)**:

- Week 2 labs (R Markdown and Tables, and Descriptive Statistics)
    - Due Monday 2/5 at 11:59pm (via P-web)
- [Homework #2](s209s24/hw2.html)
    - Due Friday 2/2 at 11:59pm (via P-web)

$~$

**Week 3**:

```{r, echo = FALSE, message = FALSE, warning = FALSE}
x = data.frame(Date = c("Mon 2/5", "Wed 2/7", "Fri 2/9"), 
               Lecture = c("[Descriptive statistics (quantitative outcomes)](s209s24/descriptive_stats2.pdf)", 
                           "[Descriptive statistics (correlation)](s209s24/descriptive_stats3.pdf)",
                           " "),
               Lab = c("[Summarizing data with `dplyr`](s209s24/dplyr.html)", 
                       " ",
                       "[Correlation and regression](s209s24/cor_reg.html)"))
kable(x) %>%
  kable_styling(bootstrap_options = c("hover"))
```

**Assignments and Deadlines (week 3)**:

- Week 3 labs (`dplyr`, correlation and regression)
    - Due Monday 2/12 at 11:59pm (via P-web)
- [Homework #3](s209s24/hw3.html)
    - Due Friday 2/9 at 11:59pm (via P-web)

$~$

**Week 4**:

```{r, echo = FALSE, message = FALSE, warning = FALSE}
x = data.frame(Date = c("Mon 2/12", "Wed 2/14", "Fri 2/16"), 
               Lecture = c("[Stratification](s209s24/strat.pdf)", 
                           " ",
                           " "),
               Lab = c("[Multivariate Relationships](s209s24/sp.html)", 
                       "[Multivariable regression (part 1)](s209s24/mreg1.html)",
                       "[Multivariable regression (part 2)](s209s24/mreg2.html)"))
kable(x) %>%
  kable_styling(bootstrap_options = c("hover"))
```

- Week 4 labs (multivariate relationships, and multivariable regression parts 1 and 2)
    - Due Monday 2/19 at 11:59pm (via P-web)
- [Homework #4](s209s24/hw4.html)
    - Due Friday 2/16 at 11:59pm (via P-web)

$~$

**Week 5**:

```{r, echo = FALSE, message = FALSE, warning = FALSE}
x = data.frame(Date = c("Mon 2/19", "Wed 2/21", "Fri 2/23"), 
               Lecture = c("[Exam 1 Review](s209s24/exam1_revq.html) ---  [sample solution](s209s24/exam1_revq_soln.html)", 
                           "Exam 1",
                           "[Sampling from a Population](s209s24/sampling.pdf)"),
               Lab = c(" ", 
                       "Exam 1",
                       "[Sampling Variability](s209s24/sampling.html)"))
kable(x) %>%
  kable_styling(bootstrap_options = c("hover"))
```

- Exam 1 will take place in *Noyce 2022* at 1pm on Wednesday 2/21
   - You may use a basic calculator (but not one that can store data).
   - A practice exam is [found here](s209s24/practice_exam1.pdf)
       - The sketch solution is [found here](s209s24/practice_exam1_soln.pdf)
   - A study guide is [found here](s209s24/Exam1_StudyGuide.pdf)
- There is no homework assignment this week due to Exam 1.
- Lab 9 (Sampling variability) will not be due until *Monday 3/4*.

$~$

### Exam #2 Content

The **sampling from a population** lecture and lab from Friday 2/23 will be a topic on Exam 2, along with the following content:

**Week 6**:

```{r, echo = FALSE, message = FALSE, warning = FALSE}
x = data.frame(Date = c("Mon 2/26", "Wed 2/28", "Fri 3/1"), 
               Lecture = c("[Interval Estimation](s209s24/intervals.pdf)",
                           " ",
                           "[Normal Approximations](s209s24/normal_ci1.pdf)"),
               Lab = c("[Bootstrapping](s209s24/conf_ints.html)", 
                       "Bootstrapping (cont.)",
                       " "))
kable(x) %>%
  kable_styling(bootstrap_options = c("hover"))
```

- Week 6 labs (bootstrapping) and Lab 9 from Friday 2/23
    - Due Monday 3/4 at 11:59pm (via P-web)
- [Homework #5](s209s24/hw5.html)
    - Due Friday 3/1 at 11:59pm (via P-web)

$~$

**Week 7**:

```{r, echo = FALSE, message = FALSE, warning = FALSE}
x = data.frame(Date = c("Mon 3/4", "Wed 3/6", "Fri 3/8"), 
               Lecture = c("[Student's $t$-distribution](s209s24/normal_ci2.pdf)",
                           " ",
                           " "),
               Lab = c(" ", "[Confidence Intervals in `R`](s209s24/conf_ints2.html)",
                       "Confidence Intervals in `R` (cont.)"))
kable(x) %>%
  kable_styling(bootstrap_options = c("hover"))
```

- Week 7 labs (confidence intervals in `R`)
    - Due Monday 3/11 at 11:59pm (via P-web)
- [Homework #6](s209s24/hw6.html)
    - Due Friday 3/8 at 11:59pm (via P-web)

$~$

**Week 8**:

```{r, echo = FALSE, message = FALSE, warning = FALSE}
x = data.frame(Date = c("Mon 3/11", "Wed 3/13", "Fri 3/15"), 
               Lecture = c("[Null hypotheses,  $p$-values, and decisions](s209s24/ht1.pdf)",
                           " ",
                           "Class Project"),
               Lab = c("", 
                       "[Randomization Tests](s209s24/ht1.html)",
                       "Class Project"))
kable(x) %>%
  kable_styling(bootstrap_options = c("hover"))
```

- Week 8 lab (Randomization Tests)
    - Due Friday 3/15 at 11:59pm (via P-web)
- [Homework #7](s209s24/hw7.html)
    - Due Friday 3/15 at 11:59pm (via P-web)

$~$

**Week 9**:

```{r, echo = FALSE, message = FALSE, warning = FALSE}
x = data.frame(Date = c("Mon 4/1", "Wed 4/3", "Fri 4/5"), 
               Lecture = c("Normal Approximations for Hypothesis Testing",
                           " ",
                           " "),
               Lab = c(" ", 
                       "[Hypothesis Testing in `R`](s209s24/ht2.html)",
                       "Hypothesis Testing in `R` (cont.)"))
kable(x) %>%
  kable_styling(bootstrap_options = c("hover"))
```


- Week 9 lab (Hypothesis Testing in `R`)
    - Due Monday 3/15 at 11:59pm (via P-web)
- [Homework #8](s209s24/hw8.html)
    - Due Friday 4/5 at 11:59pm (via P-web)

$~$

**Week 10**:

```{r, echo = FALSE, message = FALSE, warning = FALSE}
x = data.frame(Date = c("Mon 4/8", "Wed 4/10", "Fri 4/12"), 
               Lecture = c("Exam 2 Review",
                           "Exam 2",
                           "Outliers, transformations, and non-parametric tests"),
               Lab = c(" ", 
                       "Exam 2",
                       " "))
kable(x) %>%
  kable_styling(bootstrap_options = c("hover"))
```


- **Exam 2** is planned for *Wednesday 4/10* during class (1-2:20pm)
    - [Practice exam](s209s24/practice_exam2.pdf)
    - [Study guide](s209s24/Exam2_StudyGuide.pdf)
- There is no homework due this week due to Exam 2

$~$

### Exam #3 Content

Topics:

- Outliers/transformations and non-parametric tests, Chi-squared tests, ANOVA, multiple comparisons, inference for regression

$~$

## Recommended Readings

The chapters/materials listed below are resources that I recommend you read during the week provided in order to deepen your understanding of course topics and expose yourself to additional perspectives. It has been my observation that students who complete these readings have been the most successful.

- Week 1 (1/22 - 1/26):
    - IMS Ch 1.2, 1.3, 4.1, 4.2, 4.6, 5.1, 5.3, 5.5 (focus on the types of graphs discussed in Ch 4/5)
- Week 2 (1/29 - 2/2)
    - IMS Ch 1.1, 4.3, 5.2, 5.4, 5.5, 5.6 (focus on understanding numerical summaries and tables)
- Week 3 (2/5 - 2/9)
    - IMS Ch 5.5, 5.6, 7.1, 7.2, 7.3
- Week 4 (2/12 - 2/16)
    - IMS Ch 7.1, 7.2, 8.1, 8.3
- Week 5 (2/19 - 2/23)
    - None  
- Week 6 (2/26 - 3/1)
    - IMS Ch 12.1, 12.2, 12.3, 13.1, 13.2

## Project 

Information on the course project is found below:

- [This link](s209s24/final_project.html) contains the official assignment description and guidelines.
- The first due-date is Monday 3/4, you should contact me about your project group by this date

## Exams

Information about exams (including dates and study materials) will be posted here.

- **Exam 1**: Planned for *Wednesday 2/21* during class (1-2:20pm) in *Noyce 2022*
    - [Practice exam](s209s24/practice_exam1.pdf)
    - [Study guide](s209s24/Exam1_StudyGuide.pdf)
    - Solutions to the practice exam will be posted on Monday 2/19
- **Exam 2**: Tentatively planned for *Wednesday 4/10* during class (1-2:20pm)
    - [Practice exam](s209s24/practice_exam2.pdf)
    - [Study guide](s209s24/Exam2_StudyGuide.pdf)

Unless otherwise indicated, you are responsible for the content of all lectures, labs, and homework on the corresponding exam.