---
title: "STA-209 - Applied Statistics (Spring 2025)"
output:
  html_document:
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: false
---

$~$

Welcome to the course website for Sta-209 (Applied Statistics) Sections 01 and 03. You can find the course syllabus linked below:

- [Click here](syllabus209s25.html) to view the course syllabus

You can locate course content by scrolling, or by using the navigation bar in the upper left.  

Please note that some material will not be posted until we've reached that point in the course.

## Course Materials

Many class meetings involve both lab and lectures. Partners will be assigned for most labs, which will will typically be due on Mondays. Homework will typically be due on Friday at midnight (with some exceptions surrounding exams).

$~$

### Exam #1 Content

**Week 1** - Data Basics and an Introduction to `R`

```{r, echo = FALSE, message = FALSE, warning = FALSE}
library(knitr)
library(kableExtra)
library(dplyr)
# x <- cars[1:3,]
# urls <- c("stackoverflow.com", "stats.stackexchange.com", "homebrew.stackexchange.com")
# linkID <- c("link1", "link2", "link3")
# x$website <- paste0("[", linkID, "](http://", urls, ")")
# kable(x)

x = data.frame(Date = c("Mon 1/20", "Wed 1/22", "Fri 1/24"), 
               Lecture = c("No class (MLK Day)", 
                           "[Data Basics](s209s25/data_basics.pdf)",
                           "[Univariate Summaries and Visualizations](s209s25/univariate.pdf)"),
               Lab = c(" ", 
                       "[Lab 1 - Introduction to R](s209s25/R_basics.html)",
                       "[Lab 2 - Intro to `ggplot` and R Markdown](s209s25/ggplot1.html)"),
               Resources = c(" ", "[IMS Ch 1](https://openintro-ims.netlify.app/data-hello), [HOPR Ch 2](https://rstudio-education.github.io/hopr/basics.html)", " "))
knitr::kable(x, format = "html") %>%
  kable_styling(bootstrap_options = c("hover"))
```

**Assignments and Deadlines**:

- Labs 1 and 2 are due Monday 1/27 at 11:59pm
- [Homework 1](s209s25/hw1.html) is due Friday 1/24 at 11:59pm

$~$

**Week 2** - Data Visualizations and Contingency Tables

```{r, echo = FALSE, message = FALSE, warning = FALSE}
x = data.frame(Date = c("Mon 1/27", "Wed 1/29", "Fri 1/31"), 
               Lecture = c(" ", 
                           "[Contingency tables](s209s25/cont.pdf)",
                           "No class (faculty retreat)"),
               Lab = c("[Lab 3 - Bivariate Visualizations and Finding Association](s209s25/ggplot2.html)", 
                       "[Lab 4 - Contingency Tables](s209s25/ct.html)",
                       " "),
               Resources = c("[IMS Ch 4 and 5](https://openintro-ims.netlify.app/explore-categorical)", " ", " "))
knitr::kable(x, format = "html") %>%
  kable_styling(bootstrap_options = c("hover"))
```

**Assignments and Deadlines**:

- Labs 3 and 4 are due *Tuesday 2/4 at 11:59pm*
- [Homework 2](s209s25/hw2.html) is due *Friday 1/31 at 11:59pm*

$~$

**Week 3** - Correlation and Simple Linear Regression

```{r, echo = FALSE, message = FALSE, warning = FALSE}
x = data.frame(Date = c("Mon 2/3", "Wed 2/5", "Fri 2/7"), 
               Lecture = c(" ","[Correlation](s209s25/corr.pdf)", 
                           "[Simple Linear Regression](s209s25/reg.pdf)"),
               Lab = c("Finish Lab 4", 
                       "[Lab 5 - Correlation and Regression](s209s25/cor_reg.html)",
                       "Finish Lab 5"),
               Resources = c("[IMS Ch 7](https://openintro-ims.netlify.app/model-slr)", " ", " "))
knitr::kable(x, format = "html") %>%
  kable_styling(bootstrap_options = c("hover"))
```

**Assignments and Deadlines**:

- Labs 5 is due *Monday 2/10 at 11:59pm*
- [Homework 3](s209s25/hw3.html) is due *Friday 2/7 at 11:59pm*

$~$

**Week 4** - Marginal vs. Conditional Effects, Stratification, and Multivariable Linear Regression

```{r, echo = FALSE, message = FALSE, warning = FALSE}
x = data.frame(Date = c("Mon 2/10", "Wed 2/12", "Fri 2/14"), 
               Lecture = c(" ","[Multivariable Regression (part 1)](s209s25/mreg.pdf)", 
                           " "),
               Lab = c("[Lab 6 - Marginal vs. Conditional Effects and Stratification](s209s25/strat.html)", 
                       "[Lab 7 - Multivariable Regression](s209s25/mreg1.html)",
                       "Lab 7 (cont.)"),
               Resources = c(" ", "[IMS Ch 8](https://openintro-ims.netlify.app/model-mlr)",  " "))
knitr::kable(x, format = "html") %>%
  kable_styling(bootstrap_options = c("hover"))
```

**Assignments and Deadlines**:

- Labs 6 is due *Monday 2/17*
    - Lab 7 is not due until *Wednesday 2/19*
- [Homework 4](s209s25/hw4.html) is due *Friday 2/14 at 11:59pm*

$~$

**Week 5** - Multivariable Linear Regression (cont.) and Exam 1

```{r, echo = FALSE, message = FALSE, warning = FALSE}
x = data.frame(Date = c("Mon 2/17", "Wed 2/19", "Fri 2/21"), 
               Lecture = c("[Multivariable Regression (part 2)](s209s25/mr2.html)"," ", 
                           "Exam 1"),
               Lab = c("Finish Lab 7", 
                       "Exam 1 Review",
                       " "),
               Resources = c(" ", " ",  " "))
knitr::kable(x, format = "html") %>%
  kable_styling(bootstrap_options = c("hover"))
```

**Assignments and Deadlines**:

- Remember that Lab 7 is due Wednesday 2/19
- There is no homework assignment this week, use the extra time to study for Exam 1
- [Practice Version of Exam 1](s209s25/practice_exam1.pdf)
    - 
- [Study Guide for Exam 1](s209s25/exam1_study_guide.pdf)
    - You might also find [this study guide](s209s24/Exam1_StudyGuide.pdf) I wrote for last Spring's first exam helpful

$~$


### Exam #2 Content

**Week 6** - Probability and Sampling from a Population

```{r, echo = FALSE, message = FALSE, warning = FALSE}
x = data.frame(Date = c("Mon 2/24", "Wed 2/26", "Fri 2/28"), 
               Lecture = c("[Random Processes, Probability, and Sampling](s209s25/sampling.pdf)", " ", 
                           " "),
               Lab = c("[Lab 8 - Sampling](s209s25/sampling.html)", 
                       "[Lab 9 - Normal Distributions and Central Limit Theorem](s209s25/clt_ci.html)",
                       "Finish Lab 9"),
               Resources = c(" ", "[IMS Ch 13.2](https://openintro-ims.netlify.app/foundations-mathematical)",  "[3Blue1Brown Video about CLT](https://www.youtube.com/watch?v=zeJD6dqJ5lo)"))
knitr::kable(x, format = "html") %>%
  kable_styling(bootstrap_options = c("hover"))
```

**Assignments and Deadlines**:

- Labs 8 and 9 are due on Monday 3/3
- [Homework 5](s209s25/hw5.html) is due *Friday 2/28 at 11:59pm*

$~$

**Week 7** - Using Confidence Intervals to Draw Conclusions

```{r, echo = FALSE, message = FALSE, warning = FALSE}
x = data.frame(Date = c("Mon 3/3", "Wed 3/5", "Fri 3/7"), 
               Lecture = c("[Interval Estimation](s209s25/conf.pdf)", "[Student's t-distribution](s209s25/t_dist.pdf)", 
                           " "),
               Lab = c("[Lab 10 - Confidence Intervals for a Proportion](s209s25/conf_int.html)", 
                       "[Lab 11 - Confidence Intervals for Other Descriptive Statistics](s209s25/conf_int2.html)",
                       "Finish Lab 11"),
               Resources = c(" ", "[IMS Ch 12](https://openintro-ims.netlify.app/foundations-bootstrapping)",  " "))
knitr::kable(x, format = "html") %>%
  kable_styling(bootstrap_options = c("hover"))
```

- Labs 10 and 11 are due *Friday 3/7 at 11:59pm*
- [Homework 6](s209s25/hw6.html) is due *Friday 3/7 at 11:59pm*

$~$

**Week 8** - Hypothesis Testing

```{r, echo = FALSE, message = FALSE, warning = FALSE}
x = data.frame(Date = c("Mon 3/24", "Wed 3/26", "Fri 3/28"), 
               Lecture = c("[Hypothesis Tests and $p$-values](s209s25/ht1.pdf)", "[Decision Errors](s209s25/ht2.pdf)", 
                           ""),
               Lab = c(" ", 
                       "[Lab 12 - Using Simulations to find $p$-values](s209s25/ht_sim.html)",
                       "[Lab 13 - Using Probability Models to find $p$-values](s209s25/ht_model.html)"),
               Resources = c(" ", "[IMS Ch 12](https://openintro-ims.netlify.app/foundations-bootstrapping)",  " "))
knitr::kable(x, format = "html") %>%
  kable_styling(bootstrap_options = c("hover"))
```

- Lab 12 is due *Monday 3/31 at 11:59pm*
    - Lab 13 is not due until *Friday 4/4*
- [Homework 7](s209s25/hw7.html) is due *Friday 3/28 at 11:59pm*

$~$

**Week 9** - More Hypothesis Testing

```{r, echo = FALSE, message = FALSE, warning = FALSE}
x = data.frame(Date = c("Mon 3/31", "Wed 4/2", "Fri 4/4"), 
               Lecture = c("Candidate Visit (flex day)", " ", 
                           " "),
               Lab = c("", 
                       "[Lab 14 - Transformations, Outliers, and Non-parametric Tests](s209s25/ht_outliers.html)",
                       "Finish Lab 14/Exam 2 Review"),
               Resources = c(" ", " ",  " "))
knitr::kable(x, format = "html") %>%
  kable_styling(bootstrap_options = c("hover"))
```

- Lab 14 is due *Friday 4/4 at 11:59pm*
- There is no homework assignment this week, use the extra time to study for Exam 2 on Monday 4/7
- Practice materials for Exam 2
    - [Exam 2 Study Guide](s209s25/exam2_study_guide.pdf)
    - [Practice Version of Exam 2](s209s25/practice_exam2.pdf)
        - [Practice Exam Solution](s209s25/practice_exam2_soln.pdf)

$~$

**Week 10** - Exam 2 and Chi-squared Tests

```{r, echo = FALSE, message = FALSE, warning = FALSE}
x = data.frame(Date = c("Mon 4/7", "Wed 4/9", "Fri 4/11"), 
               Lecture = c("Exam 2", "[Chi-Squared Tests (part 1 - goodness of fit)](s209s25/chisq1.pdf)", "[Chi-Squared Tests (part 2 - independence)](s209s25/chisq2.pdf)"),
               Lab = c(" ", 
                       "[Lab 15 - Chi-Squared Tests](s209s25/chisq.html)",
                       "Finish Lab 15"),
               Resources = c(" ", "[IMS Ch 18](https://openintro-ims.netlify.app/inference-tables)",  " "))
knitr::kable(x, format = "html") %>%
  kable_styling(bootstrap_options = c("hover"))
```

- Lab 15 is due *Monday 4/14*
- [Homework 8](s209s25/hw8.html) is due *Monday 4/14 at 11:59pm*


$~$

### Exam #3 Content

*Note*: The topic of Chi-squared testing from Week 10 is included on Exam #3

**Week 11** - Analysis of Variance (ANOVA)

```{r, echo = FALSE, message = FALSE, warning = FALSE}
x = data.frame(Date = c("Mon 4/14", "Wed 4/16", "Fri 4/18"), 
               Lecture = c("[Analysis of Variance (ANOVA)](s209s25/anova.pdf)", " ", " "),
               Lab = c("[Lab 16 - Analysis of Variance (ANOVA)](s209s25/anova.html)", 
                       "Finish Lab 16",
                       "Project Worktime and Check-in"),
               Resources = c("[IMS Ch 22](https://openintro-ims.netlify.app/inference-many-means)", " ",  " "))
knitr::kable(x, format = "html") %>%
  kable_styling(bootstrap_options = c("hover"))
```

- Lab 16 is due *Monday 4/21*
- [Homework 9](s209s25/hw9.html) is due *Monday 4/21 by 11:59pm*
- Project exploratory analysis is due *Friday 4/18 by 11:59pm*

$~$

**Week 12** - Statistical Inference for Linear Regression Models

```{r, echo = FALSE, message = FALSE, warning = FALSE}
x = data.frame(Date = c("Mon 4/21", "Wed 4/23", "Fri 4/25"), 
               Lecture = c("[Inference for Linear Regression (F-tests)](s209s25/reg_inf.pdf)", "[Inference for Linear Regression (t-tests)](s209s25/reg_inf2.pdf)", "[Logistic Regression (part 1)](s209s25/logr1.pdf)"),
               Lab = c("[Lab 17 - Inference for Linear Regression](s209s25/reg_if.html)", 
                       "Finish Lab 17",
                       "[Lab 18 - Logistic Regression](s209s25/logr.html)"),
               Resources = c("[IMS Ch 25](https://openintro-ims.netlify.app/inf-model-mlr)", " ",  "[IMS Ch 9](https://openintro-ims.netlify.app/model-logistic)"))
knitr::kable(x, format = "html") %>%
  kable_styling(bootstrap_options = c("hover"))
```

- Lab 17 is due *Monday 4/28*
- [Homework 10](s209s25/hw10.html) is due *Friday 5/2 by 11:59pm* 

$~$

**Week 13** - Logistic Regression

```{r, echo = FALSE, message = FALSE, warning = FALSE}
x = data.frame(Date = c("Mon 4/28", "Wed 4/30", "Fri 5/2"), 
               Lecture = c("[Logistic Regression (part 2)](s209s25/logr2.pdf)", " ", "Exam 3 Review"),
               Lab = c("[Continue Lab 18](s209s25/logr.html)", 
                       "Finish Lab 18",
                       " "),
               Resources = c(" ", " ",  " "))
knitr::kable(x, format = "html") %>%
  kable_styling(bootstrap_options = c("hover"))
```

- Homework 10 is due *Friday 5/2 by 11:59pm* 
- Lab 18 is due *Friday 5/2 by 11:59pm*
- Exam 3 is on Monday 5/5
    - [Study Guide](s209s25/exam3_study_guide.pdf)
    - [Practice version of the exam](s209s25/practice_exam3.pdf)
        - [Solutions to the practice exam](s209s25/practice_exam3_soln.pdf)


$~$

**Week 14** - Exam 3 and Project Presentations


```{r, echo = FALSE, message = FALSE, warning = FALSE}
x = data.frame(Date = c("Mon 5/5", "Wed 5/7", "Fri 5/9"), 
               Lecture = c("Exam 3", "Project Presentations", "Project Presentations"),
               Lab = c(" ", 
                       " ",
                       " "),
               Resources = c(" ", " ",  " "))
knitr::kable(x, format = "html") %>%
  kable_styling(bootstrap_options = c("hover"))
```

- Exam retakes are Tuesday 5/13 from 2-5pm (Sec-01) and Wednesday from 2-5pm (Sec-03)
- Project Reports are due Wednesday 5/14 at 5pm (the end of the semester for the later section)

$~$

## Project 

Below is a description of the class project:

- [Project Description](s209s25/final_project.html)
    - ~~The first deadline is to choose your project group by Friday 2/28. Check your email for the project group form.~~
    - ~~The second deadline is to submit your project proposal by Monday 3/24. Read the project description for guidelines on what to include in your proposal.~~
    - ~~The third deadline is to complete an exploratory analysis of your data by Friday 4/18. You should prepare a brief document using R Markdown that includes descriptions of your variables, at least two data visualizations, and a set of descriptive statistics or a regression model.~~
    - Project presentations are Wednesday 5/7 and Friday 5/9 during class. Project reports are due Wednesday 5/14 at 5pm.
