---
title: "STA-209 - Applied Statistics (Fall 2025)"
output:
  html_document:
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: false
---

$~$

Welcome to the course website for Sta-209-02 (Applied Statistics). You can find the course syllabus linked below:

- [Click here](syllabus209f25.html) to view the course syllabus

You can locate course content by scrolling, or by using the navigation bar in the upper left.  

Please note that some material will not be posted until we've reached that point in the course.

## Course Materials

Course meetings typically involve a short lecture followed by a lab activity. The labs from a given week are generally due on Friday, and the corresponding homework assignment is due on the following Monday. Unless otherwise mentioned, all assignments are due by 11:59pm (midnight) on their due date.

$~$

### Exam #1 Content

**Week 0/1** - Statistical Thinking and Simple Hypothesis Tests

```{r, echo = FALSE, message = FALSE, warning = FALSE}
library(knitr)
library(kableExtra)
library(dplyr)
# x <- cars[1:3,]
# urls <- c("stackoverflow.com", "stats.stackexchange.com", "homebrew.stackexchange.com")
# linkID <- c("link1", "link2", "link3")
# x$website <- paste0("[", linkID, "](http://", urls, ")")
# kable(x)

x = data.frame(Date = c("Fri 8/29", "Mon 9/1", "Wed 9/3", "Fri 9/5"), 
               Lecture = c("[Introduction to Statistical Thinking](s209f25/intro.pdf)", 
                           "No class (Labor Day)",
                           "[Hypothesis Testing](s209f25/ht1.pdf)",
                           " "),
               Lab = c("[Lab 1 - A first hypothesis test](s209f25/first_test.html)", 
                       "  ",
                       "Finish/discuss Lab 1",
                       "[Lab 2 - Intro to `R` and one-sample categorical data](s209f25/one_sample_cat.html)"),
               Resources = c(" ", " ", "[`R` Basics from Modern Statistics with R](https://www.modernstatisticswithr.com/thebasics.html)", " "))
knitr::kable(x, format = "html") %>%
  kable_styling(bootstrap_options = c("hover"))
```

**Assignments and Deadlines**:

- Labs 1 and 2 are due Friday 9/5 by 11:59pm (submit via Canvas)
- [Homework 1](s209f25/hw1.html) is due Monday 9/8 (submit via Canvas)

$~$

**Week 2** - More Hypothesis Testing

```{r, echo = FALSE, message = FALSE, warning = FALSE}
x = data.frame(Date = c("Mon 9/8", "Wed 9/10", "Fri 9/12"), 
               Lecture = c(" ", 
                           "[One-sample Z and T tests](s209f25/ht2.pdf)",
                           " "),
               Lab = c("[Lab 3 - More `R` and one-sample quantitative data](s209f25/more_R.html)", 
                       "Finish/discuss Lab 3",
                       "[Lab 4 - One-sample hypothesis tests in `R`](s209f25/Z_and_T.html)"),
               Resources = c("[Data visualization from R for Data Science](https://r4ds.hadley.nz/layers.html) and [`ggplot` Cheatsheet](https://posit.co/wp-content/uploads/2022/10/data-visualization-1.pdf)", "[IMS Z-test for a single proportion](https://openintro-ims.netlify.app/inference-one-prop#hypothesis-test-for-a-proportion)", " "))
knitr::kable(x, format = "html") %>%
  kable_styling(bootstrap_options = c("hover"))
```

**Assignments and Deadlines**:

- Lab 3 is due Friday 9/12 by 11:59pm
- Lab 4 is due Monday 9/15 by 11:59pm
- [Homework 2](s209f25/hw2.html) is due Monday 9/15 by 11:59pm

$~$

**Week 3** - Two-sample Tests

```{r, echo = FALSE, message = FALSE, warning = FALSE}
x = data.frame(Date = c("Mon 9/15", "Wed 9/17", "Fri 9/19"), 
               Lecture = c("", 
                           "[Two-sample Z and T tests](s209f25/ht3.pdf)",
                           " "),
               Lab = c("Finish/discuss Lab 4", 
                       "[Lab 5 - Analyzing two-sample data in `R`](s209f25/two_sample.html)",
                       "Finish/discuss Lab 5"),
               Resources = c(" " , " ", " "))
knitr::kable(x, format = "html") %>%
  kable_styling(bootstrap_options = c("hover"))
```

- Lab 5 is due Monday 9/22 at 11:59pm
- [Homework 3](s209f25/hw3.html) is due Monday 9/22 by 11:59pm

$~$

**Week 4** - Correlation and Regression

```{r, echo = FALSE, message = FALSE, warning = FALSE}
x = data.frame(Date = c("Mon 9/22", "Wed 9/24", "Fri 9/26"), 
               Lecture = c("[Correlation](s209f25/cor.pdf)", 
                           "[Simple Linear Regression](s209f25/reg.pdf)",
                           " "),
               Lab = c("", 
                       "[Lab 6 - Correlation and Simple Linear Regression](s209f25/cor_reg.html)",
                       "Finish/discuss Lab 6"),
               Resources = c(" " , " ", " "))
knitr::kable(x, format = "html") %>%
  kable_styling(bootstrap_options = c("hover"))
```

- Lab 6 is due Monday 9/29
- [Homework 4](s209f25/hw4.html) is due Monday 9/29
- We have our first exam next week ([practice version](s209f25/Exam1_Practice.pdf))
    - [Exam 1 study guide](s209f25/Exam_1_study_guide.pdf) 

$~$ 

**Week 5** - Wrap-up and Exam 1

```{r, echo = FALSE, message = FALSE, warning = FALSE}
x = data.frame(Date = c("Mon 9/29", "Wed 10/1", "Fri 10/3"), 
               Lecture = c("[Study Design and Contingency Tables](s209f25/design.pdf)", 
                           " ",
                           "Exam 1"),
               Lab = c(" ", 
                       "Review Session",
                       " "),
               Resources = c(" " , " ", " "))
knitr::kable(x, format = "html") %>%
  kable_styling(bootstrap_options = c("hover"))
```

- [Practice Exam 1](s209f25/Exam1_Practice.pdf) 
   - [Practice Exam Solutions](s209f25/Exam1_soln.pdf) 

$~$ 

### Exam #2 Content

**Week 6** - Contingency Tables and Chi-Squared Tests

```{r, echo = FALSE, message = FALSE, warning = FALSE}
x = data.frame(Date = c("Mon 10/6", "Wed 10/8", "Fri 10/10"), 
               Lecture = c("[Study Design and Contingency Tables (continued)](s209f25/design.pdf)", 
                           "Chi-squared Tests (part 1 - Goodness of Fit)",
                           "Chi-squared Tests (part 2 - Testing Independence"),
               Lab = c("[Lab 7 - Contingency Tables](s209f25/tables.html)", 
                       "Lab 8 - Chi-squared Tests",
                       "Finish/discuss Lab 8"),
               Resources = c(" " , " ", " "))
knitr::kable(x, format = "html") %>%
  kable_styling(bootstrap_options = c("hover"))
```

- Lab 6 is due Friday 10/10
- Lab 7 is due Monday 10/13
- [Homework 5](s209f25/hw5.html) is due Monday 10/13

$~$

**Week 7**: Analysis of Variance

```{r, echo = FALSE, message = FALSE, warning = FALSE}
x = data.frame(Date = c("Mon 10/13", "Wed 10/15", "Fri 10/17"), 
               Lecture = c(" ", 
                           " ",
                           " "),
               Lab = c(" ", 
                       " ",
                       " "),
               Resources = c(" " , " ", " "))
knitr::kable(x, format = "html") %>%
  kable_styling(bootstrap_options = c("hover"))
```

$~$

 **Week 8**: Multiple Comparisons and Data Transformations

```{r, echo = FALSE, message = FALSE, warning = FALSE}
x = data.frame(Date = c("Mon 10/27", "Wed 10/29", "Fri 10/31"), 
               Lecture = c(" ", 
                           " ",
                           " "),
               Lab = c(" ", 
                       " ",
                       " "),
               Resources = c(" " , " ", " "))
knitr::kable(x, format = "html") %>%
  kable_styling(bootstrap_options = c("hover"))
```

**Week 9**: Confidence Intervals

```{r, echo = FALSE, message = FALSE, warning = FALSE, eval = FALSE}
x = data.frame(Date = c("Mon 11/3", "Wed 11/5", "Fri 11/7"), 
               Lecture = c(" ", 
                           " ",
                           " "),
               Lab = c(" ", 
                       " ",
                       " "),
               Resources = c(" " , " ", " "))
knitr::kable(x, format = "html") %>%
  kable_styling(bootstrap_options = c("hover"))
```


$~$

## Tentative Exam Dates

- Exam 1 - Friday 10/3
- Exam 2 - Friday 11/14
- Exam 3 - Monday 12/8

$~$

## Project 

Information and deadlines for the course project are [found here](s209f25/project.html)

- The first deadline is to decide upon your group members (2 or 3 people per group) by Monday 10/6
- The second deadline will be to submit a proposal for your project topic by Friday 10/10