---
title: "STA-209 - Applied Statistics (Spring 2024)"
output:
  html_document:
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: false
---

$~$

Welcome to the course website for Sta-209-04 (Applied Statistics). You can find the course syllabus linked below:

- [Click here](syllabus209s24.html) to view the course syllabus

You can locate course content by scrolling, or by using the navigation bar in the upper left.  

Please note that some material will not be posted until we've reached that point in the course.

## Course Materials

Most class meetings involve both lecture and lab components. Partners will be assigned for each lab. Labs will generally be due 1-2 class meetings after they are assigned, while homework is consistently due every Friday at midnight (with some exceptions surrounding exams).

$~$

### Exam #1 Content

**Week 1**:

```{r, echo = FALSE, message = FALSE, warning = FALSE}
library(knitr)
library(kableExtra)
library(dplyr)
# x <- cars[1:3,]
# urls <- c("stackoverflow.com", "stats.stackexchange.com", "homebrew.stackexchange.com")
# linkID <- c("link1", "link2", "link3")
# x$website <- paste0("[", linkID, "](http://", urls, ")")
# kable(x)

x = data.frame(Date = c("Mon 1/22", "Wed 1/24", "Fri 1/26"), 
               Lecture = c("[Data Basics](s209s24/data_basics.pdf)", 
                           "[Data Visualization](s209s24/data_viz.pdf)",
                           " "),
               Lab = c("[Introduction to `R`](s209s24/R_basics.html)", 
                       "[Data Visualization (part 1)](s209s24/ggplot1.html)",
                       "Data Visualization (part 2)"))
kable(x) %>%
  kable_styling(bootstrap_options = c("hover"))
```

**Assignments and Deadlines (week 1)**:

- The Introduction to `R` and Data Visualization labs
    - Due ~~Monday 1/29~~ Wednesday 1/31 at 11:59pm (via P-web)
- [Homework 1](s209s24/hw1.html) 
    - Due ~~Friday 1/26~~ Tuesday 1/30 at 11:59pm (via P-web)

$~$

**Week 2**:

```{r, echo = FALSE, message = FALSE, warning = FALSE}
library(knitr)
library(kableExtra)
library(dplyr)
# x <- cars[1:3,]
# urls <- c("stackoverflow.com", "stats.stackexchange.com", "homebrew.stackexchange.com")
# linkID <- c("link1", "link2", "link3")
# x$website <- paste0("[", linkID, "](http://", urls, ")")
# kable(x)

x = data.frame(Date = c("Mon 1/29", "Wed 1/31", "Fri 2/2"), 
               Lecture = c("", 
                           "[Descriptive statistics (categorical data)](s209s24/descriptive_stats.pdf)",
                           "Descriptive statistics (quantitative data)"),
               Lab = c("[Extra credit lab](s209s24/ggplot2.html)", 
                       "[R Markdown and Tables](s209s24/tables.html)",
                       "Descriptive statistics and `dplyr` (part 2)"))
kable(x) %>%
  kable_styling(bootstrap_options = c("hover"))
```

**Assignments and Deadlines (week 2)**:

- Week 2 labs (R Markdown and Tables, and Descriptive Statistics)
    - Due Monday 2/5 at 11:59pm (via P-web)
- [Homework #2](s209s24/hw2.html)
    - Due Friday 2/2 at 11:59pm (via P-web)

$~$

### Exam #2 Content

Coming soon

$~$

### Exam #3 Content

Coming soon

$~$

## Recommended Readings

The chapters/materials listed below are resources that I recommend you read during the week provided in order to deepen your understanding of course topics and expose yourself to additional perspectives. It has been my observation that students who complete these readings have been the most successful.

- Week 1 (1/22 - 1/26):
    - IMS Ch 1.2, 1.3, 4.1, 4.2, 4.6, 5.1, 5.3, 5.5 (focus on the types of graphs discussed in Ch 4/5)
- Week 2 (1/29 - 2/2)
    - IMS Ch 1.1, 4.3, 5.2, 5.4, 5.5, 5.6 (focus on understanding numerical summaries and tables)

## Project 

Information about the course project will be posted here at a later date.

## Exams

Information about exams (including dates and study materials) will be posted here.

Unless otherwise indicated you are responsible for the content of all lectures and labs on the corresponding exam.