---
title: "STA-209 - Applied Statistics (Spring 2025)"
output:
  html_document:
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: false
---

$~$

Welcome to the course website for Sta-209 (Applied Statistics) Sections 01 and 03. You can find the course syllabus linked below:

- [Click here](syllabus209s25.html) to view the course syllabus

You can locate course content by scrolling, or by using the navigation bar in the upper left.  

Please note that some material will not be posted until we've reached that point in the course.

## Course Materials

Many class meetings involve both lab and lectures. Partners will be assigned for most labs, which will will typically be due on Mondays. Homework will typically be due on Friday at midnight (with some exceptions surrounding exams).

$~$

### Exam #1 Content

**Week 1** - Data Basics and an Introduction to `R`

```{r, echo = FALSE, message = FALSE, warning = FALSE}
library(knitr)
library(kableExtra)
library(dplyr)
# x <- cars[1:3,]
# urls <- c("stackoverflow.com", "stats.stackexchange.com", "homebrew.stackexchange.com")
# linkID <- c("link1", "link2", "link3")
# x$website <- paste0("[", linkID, "](http://", urls, ")")
# kable(x)

x = data.frame(Date = c("Mon 1/20", "Wed 1/22", "Fri 1/24"), 
               Lecture = c("No class (MLK Day)", 
                           "[Data Basics](s209s25/data_basics.pdf)",
                           "[Univariate Summaries and Visualizations](s209s25/univariate.pdf)"),
               Lab = c(" ", 
                       "[Lab 1 - Introduction to R](s209s25/R_basics.html)",
                       "[Lab 2 - Intro to `ggplot` and R Markdown](s209s25/ggplot1.html)"),
               Resources = c(" ", "[IMS Ch 1](https://openintro-ims.netlify.app/data-hello), [HOPR Ch 2](https://rstudio-education.github.io/hopr/basics.html)", " "))
kable(x) %>%
  kable_styling(bootstrap_options = c("hover"))
```

**Assignments and Deadlines**:

- Labs 1 and 2 are due Monday 1/27 at 11:59pm
- [Homework 1](s209s25/hw1.html) is due Friday 1/24 at 11:59pm

$~$

**Week 2** - Data Visualizations and Contingency Tables

```{r, echo = FALSE, message = FALSE, warning = FALSE}
x = data.frame(Date = c("Mon 1/27", "Wed 1/29", "Fri 1/31"), 
               Lecture = c(" ", 
                           "[Contingency tables](s209s25/cont.pdf)",
                           "No class (faculty retreat)"),
               Lab = c("[Lab 3 - Bivariate Visualizations and Finding Association](s209s25/ggplot2.html)", 
                       "[Lab 4 - Contingency Tables](s209s25/ct.html)",
                       " "),
               Resources = c("[IMS Ch 4 and 5](https://openintro-ims.netlify.app/explore-categorical)", " ", " "))
kable(x) %>%
  kable_styling(bootstrap_options = c("hover"))
```

**Assignments and Deadlines**:

- Labs 3 and 4 are due *Monday 2/3 at 11:59pm*
- [Homework 2](s209s25/hw2.html) is due *Friday 1/31 at 11:59pm*

$~$

**Week 3** - Correlation and Simple Linear Regression

$~$

**Week 4** - Marginal vs. Conditional Effects, Stratification, and Multivariable Linear Regression

$~$

**Week 5** - Multivariable Linear Regression (cont.) and Exam 1

$~$


### Exam #2 Content

*Coming soon*

$~$

### Exam #3 Content

*Coming soon*

$~$

## Project 

Information about the project will be posted here after Exam 1.

## Exams

Information about exams (including dates and study materials) will be posted here.

- You may anticipate **Exam 1** being approximately 4-5 weeks into the semester. A practice exam will be posted closer to the precise exam date.
    
Unless otherwise indicated, you are responsible for the content of all lectures, labs, and homework on the corresponding exam.