---
title: "STA-209 - Applied Statistics (Spring 2024)"
output:
  html_document:
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: false
---

$~$

### Syllabus

Welcome to the course website for Sta-209-04 (Applied Statistics). You can find the course syllabus linked below:

- [Click here](syllabus395s23.html) to view the course syllabus

You can locate course content by scrolling, or by using the navigation bar in the upper left.  

Please note that some material will not be posted until we've reached that point in the course.

## Course Materials

Most class meetings involve both lecture and lab components. Partners will be assigned for each lab. Labs will generally be due 1-2 class meetings after they are assigned, while homework is consistently due every Friday at midnight (with some exceptions surrounding exams).

$~$

### Exam #1 Content

**Week 1**:

```{r, echo = FALSE, message = FALSE, warning = FALSE}
library(knitr)
library(kableExtra)
library(dplyr)
# x <- cars[1:3,]
# urls <- c("stackoverflow.com", "stats.stackexchange.com", "homebrew.stackexchange.com")
# linkID <- c("link1", "link2", "link3")
# x$website <- paste0("[", linkID, "](http://", urls, ")")
# kable(x)

x = data.frame(Date = c("Mon 1/22", "Wed 1/24", "Fri 1/26"), 
               Lecture = c("[Data Basics](s209s24/base.pdf)", 
                           "[Data Visualization](s209s24/viz.pdf)",
                           " "),
               Lab = c("[Introduction to `R`](ml23/base_lab.html)", 
                       "[Data Visualization (part 1)](ml23/viz_lab1.html)",
                       "[Data Visualization (part 2)](ml23/viz_lab2.html)"))
kable(x) %>%
  kable_styling(bootstrap_options = c("hover"))
```

**Assignments and Deadlines**:

- The Introduction to `R` and Data Visualization (parts 1 & 2) labs are Monday 1/29 (via P-web)
- Homework 1 is due Friday 1/26 (via P-web)

**Week 2**:

```{r, echo = FALSE, message = FALSE, warning = FALSE}
library(knitr)
library(kableExtra)
library(dplyr)
# x <- cars[1:3,]
# urls <- c("stackoverflow.com", "stats.stackexchange.com", "homebrew.stackexchange.com")
# linkID <- c("link1", "link2", "link3")
# x$website <- paste0("[", linkID, "](http://", urls, ")")
# kable(x)

x = data.frame(Date = c("Mon 1/29", "Wed 1/31", "Fri 2/2"), 
               Lecture = c("[Numerical Summaries](s209s24/num.pdf)", 
                           "[Contingency Tables](s209s24/viz.pdf)",
                           " "),
               Lab = c("[Data summarization (part 1)](ml23/dsum1.html)", 
                       "[Data summarization (part 2)](ml23/dsum2.html)",
                       "[Multivariate relationships](ml23/mv.html)"))
kable(x) %>%
  kable_styling(bootstrap_options = c("hover"))
```

**Assignments and Deadlines**:

- TBD

$~$

### Exam #2 Content

Coming soon

$~$

### Exam #3 Content

Coming soon

$~$

## Recommended Readings

These 

## Project 

Information about the course project will be posted here

## Exams

Information about exams (including dates and practice materials) will be posted here.

Unless otherwise indicated you are responsible for the content of all lectures and labs in a unit on its corresponding exam.