---
title: "STA-209 - Applied Statistics (Spring 2025)"
output:
  html_document:
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: false
---

$~$

Welcome to the course website for Sta-209 (Applied Statistics) Sections 01 and 03. You can find the course syllabus linked below:

- [Click here](syllabus209s25.html) to view the course syllabus

You can locate course content by scrolling, or by using the navigation bar in the upper left.  

Please note that some material will not be posted until we've reached that point in the course.

## Course Materials

Many class meetings involve both lab and lectures. Partners will be assigned for most labs, which will will typically be due on Mondays. Homework will typically be due on Friday at midnight (with some exceptions surrounding exams).

$~$

### Exam #1 Content

**Week 1** - Data Basics and an Introduction to `R`

```{r, echo = FALSE, message = FALSE, warning = FALSE}
library(knitr)
library(kableExtra)
library(dplyr)
# x <- cars[1:3,]
# urls <- c("stackoverflow.com", "stats.stackexchange.com", "homebrew.stackexchange.com")
# linkID <- c("link1", "link2", "link3")
# x$website <- paste0("[", linkID, "](http://", urls, ")")
# kable(x)

x = data.frame(Date = c("Mon 1/20", "Wed 1/22", "Fri 1/24"), 
               Lecture = c("No class (MLK Day)", 
                           "[Data Basics](s209s25/data_basics.pdf)",
                           "[Univariate Summaries and Visualizations](s209s25/univariate.pdf)"),
               Lab = c(" ", 
                       "[Lab 1 - Introduction to R](s209s25/R_basics.html)",
                       "[Lab 2 - Intro to `ggplot` and R Markdown](s209s25/ggplot1.html)"),
               Resources = c(" ", "[IMS Ch 1](https://openintro-ims.netlify.app/data-hello), [HOPR Ch 2](https://rstudio-education.github.io/hopr/basics.html)", " "))
kable(x) %>%
  kable_styling(bootstrap_options = c("hover"))
```

**Assignments and Deadlines**:

- Labs 1 and 2 are due Monday 1/27 at 11:59pm
- [Homework 1](s209s25/hw1.html) is due Friday 1/24 at 11:59pm

$~$

**Week 2** - Data Visualizations and Contingency Tables

```{r, echo = FALSE, message = FALSE, warning = FALSE}
x = data.frame(Date = c("Mon 1/27", "Wed 1/29", "Fri 1/31"), 
               Lecture = c(" ", 
                           "[Contingency tables](s209s25/cont.pdf)",
                           "No class (faculty retreat)"),
               Lab = c("[Lab 3 - Bivariate Visualizations and Finding Association](s209s25/ggplot2.html)", 
                       "[Lab 4 - Contingency Tables](s209s25/ct.html)",
                       " "),
               Resources = c("[IMS Ch 4 and 5](https://openintro-ims.netlify.app/explore-categorical)", " ", " "))
kable(x) %>%
  kable_styling(bootstrap_options = c("hover"))
```

**Assignments and Deadlines**:

- Labs 3 and 4 are due *Tuesday 2/4 at 11:59pm*
- [Homework 2](s209s25/hw2.html) is due *Friday 1/31 at 11:59pm*

$~$

**Week 3** - Correlation and Simple Linear Regression

```{r, echo = FALSE, message = FALSE, warning = FALSE}
x = data.frame(Date = c("Mon 2/3", "Wed 2/5", "Fri 2/7"), 
               Lecture = c(" ","[Correlation](s209s25/corr.pdf)", 
                           "[Simple Linear Regression](s209s25/reg.pdf)"),
               Lab = c("Finish Lab 4", 
                       "[Lab 5 - Correlation and Regression](s209s25/cor_reg.html)",
                       "Finish Lab 5"),
               Resources = c("[IMS Ch 7](https://openintro-ims.netlify.app/model-slr)", " ", " "))
kable(x) %>%
  kable_styling(bootstrap_options = c("hover"))
```

**Assignments and Deadlines**:

- Labs 5 is due *Monday 2/10 at 11:59pm*
- [Homework 3](s209s25/hw3.html) is due *Friday 2/7 at 11:59pm*

$~$

**Week 4** - Marginal vs. Conditional Effects, Stratification, and Multivariable Linear Regression

```{r, echo = FALSE, message = FALSE, warning = FALSE}
x = data.frame(Date = c("Mon 2/10", "Wed 2/12", "Fri 2/14"), 
               Lecture = c(" ","Multivariable Regression (part 1)", 
                           "Multivariable Regression (part 2)"),
               Lab = c("Lab 6 - Marginal vs. Conditional Effects and Stratification", 
                       "Lab 7 - Multivariable Regression",
                       "Finish Lab 7"),
               Resources = c(" ", "[IMS Ch 8](https://openintro-ims.netlify.app/model-mlr)",  " "))
kable(x) %>%
  kable_styling(bootstrap_options = c("hover"))
```

- Labs 6 and 7 are due *Monday 2/17*
- [Homework 4](s209s25/hw4.html) is due *Friday 2/14 at 11:59pm*

$~$

**Week 5** - Multivariable Linear Regression (cont.) and Exam 1

```{r, echo = FALSE, message = FALSE, warning = FALSE}
x = data.frame(Date = c("Mon 2/17", "Wed 2/19", "Fri 2/21"), 
               Lecture = c("Multivariable Regression (part 3)"," ", 
                           "Exam 1"),
               Lab = c("Lab 8 - ", 
                       "Exam 1 Review",
                       " "),
               Resources = c(" ", " ",  " "))
kable(x) %>%
  kable_styling(bootstrap_options = c("hover"))
```


- Lab 8 is due *Wednesday 2/19*
- There is no homework assignment this week, use the extra time to study for Exam 1
- A practice version of Exam 1 will be posted here soon, solutions will be posted immediately before class on Wednesday 2/19

$~$


### Exam #2 Content

*Coming soon*

$~$

### Exam #3 Content

*Coming soon*

$~$

## Project 

Information about the project will be posted here after Exam 1.

