---
title: "Teaching"
---

Teaching has long been a passion of mine and throughout my career I've taught numerous courses in a variety of academic settings.  I began as a high school math teacher before attending graduate school, were I served as both a teaching assistant and course instructor for Introduction to Biostatistics at the University of Iowa.  Most recently I've taught classes in applied statistics and data science at Grinnell College.  Content from the most recent iteration of these courses can be found below.  

### STA-209 - Applied Statistics - Grinnell College

STA-209 is an introductory course in applied statistics covering topics including: data collection, visualization, summary statistics, basic statistical inference for one and two samples, linear regression (simple and multiple), one- and two-way ANOVA, and categorical data analysis.  The class involves several comprehensive labs that guide students through the analysis of real data using Minitab and StatKey software. Materials from the most recent verision of the course can be found below:

```{r, echo = FALSE}
df209 <- data.frame(Topic = c(paste0("[Introduction](s209/h1.1.pdf)"), paste0("[Samples and Populations](s209/h1.2.pdf)"), "Describing Data (summary statistics and graphs)",  paste0("[Experiments and Observational Studies](s209/h1.3.pdf)"), paste0("[Describing Data (correlation and regression)](s209/h2.5.pdf)"), paste0("[Sampling Distributions](s209/h3.1.pdf)"), paste0("[Confidence Intervals (bootstrapping)](s209/h3.2.pdf)"), paste0("[Hypothesis Testing (randomization tests)](s209/h4.1.pdf)"), paste0("[Normal Distributions and Central Limit Theorem](s209/h5.1.pdf)"), paste0("[One-sample Statistical Inference](h6.1.pdf)"), paste0("[Two-sample Statistical Inference](s209/h6.3.pdf)"), paste0("[Chi-squared Tests](s209/h7.pdf)"), paste0("[Observational Designs and Association](s209/h.7sup.pdf)"), paste0("[Analysis of Variance](s209/h.8.pdf)"), paste0("[Regression (one explanatory variable)](s209/h9.pdf)"), paste0("[Regression (multiple explanatory variables)](s209/h.10.pdf)")), 
                 Lab = c(" ", " ",  paste0("[Lab #1](s209/lab1.pdf)"), " ",  paste0("[Lab #2](s209/lab2.pdf)"), " ",  paste0("[Lab #3](s209/lab3.pdf)"),  paste0("[Lab #4](s209/lab4.pdf)"),  paste0("[Lab #5](s209/lab5.pdf)"), " ", paste0("[Lab #6](s209/lab6.pdf)"), " ", " ",  paste0("[Lab #7](s209/lab7.pdf)"), " ",  paste0("[Lab #8](s209/lab8.pdf)")),
Data = c(paste0("[HappyPlanet](s209/HappyPlanet.csv)", ", ", "[AntiquitiesAct](s209/AntiquitiesAct.csv)"), " ", paste0("[ClassSurvey](s209/ClassSurvey.csv)"), paste0("[FloridaDeathPenalty](s209/FloridaDeathPenalty.csv)"), 
 paste0("[ElectionMargin](s209/ElectionMargin.csv)", ", ", "[IowaCityHomeSales](s209/IowaCityHomeSales.csv)"), " ", "[SmallColleges](s209/CollegeData.csv)", " ", " ", " ", paste0("[LeadIQ](s209/LeadIQ.csv)", ", " , "[HollywoodMovies](s209/HollywoodMovies.csv)", ", ", "[GoldenStateWarriors](s209/GSWarriors.csv)"), " ", " ", paste0("[Tailgating](s209/Tailgating.csv)", ", " , "[CommuteTracker](s209/CommuteTracker.csv)"), paste0("[ProfessorEvaluations](s209/UT-Austin_Professors.csv)"), paste0("[ProfessorSalaries](s209/Salaries.csv)", ", ", "[BreastCancer](s209/Breast_Cancer_Data.csv)")))
#library(knitr)
knitr::kable(df209)
```

### STA-230 - Introduction to Data Science - Grinnell College

STA-230 introduces core topics in data science using the R programming langauge. The course covers data cleaning, merging, exploration, visualization, modeling, and other topics using guided labs and case studies in a workshop style classroom.  Materials from the most recent version of the course are provided below, many of these materials were created by Shonda Kuiper (Grinnell College), Adam Loy (Lawrence University), and Laura Chihara (Carleton College) under ACM and Teagle foundation grants.  See the 2017 USCOTS [Data Science for Statistics webpage](https://ds4stats.github.io/uscots2017/) or Shonda Kuiper's [R Tutorials webpage](http://web.grinnell.edu/individuals/kuipers/stat2labs/RTutorials.html) for details.

```{r, echo = FALSE}
df230 <- data.frame(Topic = c("Describing Data", "Introduction to R", "Tidying Data","Data Wrangling", "Merging Data", "Data Visualization with ggplot", "Creating Maps with ggplot", "Custom Maps using Shapefiles", "Manipulating Text Strings", "Working with Dates and Times", "Data Scraping", "Unsupervised Learning (Principle Components Analysis)", "Unsupervised Learning (Clustering)", "Model Validation", "Supervised Learning (Regression)", "Supervised Learning (CART)", "Supervised Learning (Random Forest)", "Interactive Visuals with RShiny"),
Data = " ", Resources = " ")
#library(knitr)
knitr::kable(df230)
```

### BIOS-4120 - Introduction to Biostatistics - University of Iowa

BIOS-4120 is an introductory statistics course that covers basic statistical concepts and methods that are frequently used in medicine, public health, and the biological sciences.  Some topics covered include study design, descriptive statistics, basic rules of probability, measures of association, hypothesis testing for one and two sample continuous and categorical data, confidence intervals, correlation, and an introduction to regression.

### Calculus I, Algebra II with Trig, Algebra I - Pawnee High School (IL)

At the high school level I've taught: Calc I - covering limits, derivatives/anti-derivatives, finding minima and maxima, and applications; Algebra II with Trig - covering functions, graphs, exponents and logarithms, and trigonometry; Algebra I - covering order of operations, equations, and inequalities. 