---
title: "Homework #2"
author: "Your_Name_Here"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(ggplot2)
library(dplyr)
library(tidyr)
```

### Directions

For this assignment you should edit the "author" of the header to include your name.  You should save your file as "HW2_Your_Name.Rmd" before knitting.

For each of the questions you should write or add code to the blocks provided.  You should answer questions in the section following the code blocks.

If code for a question has been provided and you were not asked to modify it, please do not delete it or your .Rmd file might not knit properly.

#### Question #1 (tidy data, data wrangling, ggplot)

The data.frame `economics` in the `ggplot2` package contains US economic data provided by [US federal reserve](https://fred.stlouisfed.org/).

In the chunk below, write code that uses `ggplot` to create a line graph which displays the variables `uempmed` and `psavert` on the y-axis and `date` on the x-axis.  Use the `color` aesthetic to differentiate the lines of each variables. 

In the space below your code, use your visual to briefly describe whether these variables appear to be related.

Hints: 

- You need to tidy the `economics` data.frame before you can construct this graph
- You can use the `select` function to remove unnecessary variables as the first step in tidying

```{r}
library(ggplot2)  # Make sure you have this package installed
data("economics")

## Your code for question 1 goes here
```

Your written answer to question 1 should go here.

*indicate any help you received on this question here*




#### Question #2 (data wrangling and ggplot)

The data.frame `ChickWeight` in the `datasets` package contains data from an experiment studying the effects of different diets on the growth rate of chicks (young chickens).

In the code chunk below, write code that constructs a data.frame named "chick_df" that contains the *mean weight* for each diet group *at each time-point* using the `group_by` and `summarize` functions in the `dplyr` package. (Hint: you can group by more than one variable in the `group_by` function)

Then, use `ggplot` to construct a line plot displaying the mean weight of each diet group over time. (Hint: You shouldn't be using `geom_smooth` to make your plot, you should plot the means directly).

Below your code, briefly discuss whether there is enough information in your plot to conclude that Diet #3 leads to the most growth.

```{r}
library(datasets)  # Make sure you have this package installed
data("ChickWeight")

## Your code for question 2 goes here
```

Your written answer to question 2 should go here

*indicate any help you received on this question here*




#### Question #3 (simple-to-complex, smoothing, and ggplot)

The data.frame `diamonds` in the `ggplot2` package contains the prices and attributes of nearly 54,000 diamonds sold by an online retailer.

In the code chunk below, write code to that filters these data to contain only diamonds with prices less than $2,000, and then uses `ggplot` to construct a scatterplot displaying the relationship between the variables `carat` and `price`.  

Color the points in your scatterplot based upon the variable `cut`, and add loess smoothers using the arguments `method = "loess"` and `se = FALSE`.

In the space below your code/plot answer the following:

A) Is the information in the variable `cut` useful in understanding the price of a diamond? Could the variable `cut` be simplified (ie: could some categories be combined) and still accurately convey the trends in the data?
B) How does `carat` relate to price? Do you believe the loess smoother is necessary, or could the relationship be simplified by using a linear regression line as a smoother?


```{r}
data("diamonds")

## Your code for question 3 goes here
```

Your written answer to question 3 should go here

*indicate any help you received on this question here*


#### Question #4 (density, ggplot)

The data.frame `faithful` in the `datasets` package documents eruptions of the "Old Faithful" geyser at Yellowstone National Park in Wyoming.  The variable `eruptions` records the eruption duration (in minutes), and the variable `waiting` records the waiting time until the next eruption (also in minutes).

In the code chunk below write code that uses `ggplot` to create a two-dimensional density plot depicting the relationship between an eruption's duration (the variable `eruptions`) and the time until the next eruption (the variable `waiting`).

In the space below your code/plot answer the following:

A) Are `eruptions` and `waiting` related? What combinations of these variables are commom/uncommon?
B) What can you learn from this plot that you couldn't learn from the slope and intercept of a regression line?

```{r}
data("faithful")

## Your code for question 4 goes here
```

Your written answers to question 4 should go here

*indicate any help you received on this question here*



#### Question #5 (merging/joining, ggplot, density)

[Sean Lahman](https://en.wikipedia.org/wiki/Sean_Lahman) complied a comprehensive database containing pitching, hitting, and fielding statistics from all Major League Baseball games from 1871 through 2016.  The database is available in the package `Lahman` and contains several tables.  The data.frame "Master" contains one row per unique player.

After loading the `Lahman` database, use merging, and joining to answer the following questions:

A) Use the appropriate join to create a data.frame named "no_salary" that contains players from the "Master" data.frame that *don't match* any of the entries in the "Salaries" data.frame
B) What proportion of the players without a salary did not appear in a game (ie: don't have a record in the "Appearances" data.frame)? 
C) Is it possible that players without a salary played before the modern era? To answer this question, compare the density of the variable `birthYear` in the "no_salary" data.frame you created with the density of `birthYear` for players who had a salary.  Write code to construct this plot and write 1-2 sentences answering this question in the space below your code/plot. 

```{r}
library(Lahman)  ## Make sure you have this package installed

## Dimensions of some of the data.frames
dim(Master)
dim(Salaries)
dim(Appearances)

## Part A Code Goes Below


## Part B Code Goes Below


## Part C Code Goes Below


```

Your written answers to question 5 should go here

*indicate any help you received on this question here*




#### Question #6 (data wrangling, plotly)

The Happy Planet Index is an attempt to measure how well nations are doing at achieving long, happy, and sustainable lives for their citizens using data compiled from various sources. A description of the dataset's variable can be found [on slide 11 here](https://remiller1450.github.io/s209f19/intro_h.pdf)

For this question, use the `plot_ly` function in the `plotly` package to construct a scatterplot of "LifeExpectancy" versus "Happiness" where each country is colored by it's region. Add hover text displaying the country represented by that data-point.

Your plot should be professional in appearance, which means the region variable *should not* be displayed as a numeric code, and the axes should be labeled appropriately.

```{r}
HappyPlanet <- read.csv("https://remiller1450.github.io/data/HappyPlanet.csv")

## Your code for question 6 goes here
```

*indicate any help you received on this question here*